---
title: "Processing_2021"
author: "Marion Nyberg"
date: "05/03/2021"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, root.dir = '~/Google Drive/Micromet Lab/People/2019-Marion Nyberg/BB1-2')

library(caret)
library(leaps)
#library(MASS)
library(car)
library(dplyr)
library(plyr)
library(ggplot2)
library(lubridate)
library(naniar)
library(tidyr)
library(plotly)
library(knitr)
library(data.table)
library(kableExtra)
library(ggsci)
library(effects)
library(broom)
library(jtools)
library(MuMIn)
library(ggpubr)
library(viridis)


rm(list=ls())
```

```{r set working directory and load data}
wd <- '~/Google Drive/Micromet Lab/People/2019-Marion Nyberg/BB1-2'
setwd(wd)

Env.input_file <- "data/Full.csv" #import all data (GS and NGS), below 2 new data frames separated into GS and NGS
Env.input_data <- read.csv(Env.input_file) 

ind.GS <- (Env.input_data$jday >= 92 & Env.input_data$jday <= 274)
ind.NGS <- (Env.input_data$jday < 92 | Env.input_data$jday >=275)

Env.input_data$Period <- " "
Env.input_data$Period[ind.GS] <- "GS"
Env.input_data$Period[ind.NGS] <- "NGS"

Env.input_data$Site <- revalue(Env.input_data$Site, c("BB1"="CA-DBB", "BB2"="CA-DB2")) #rename factors

CA_DBB <- Env.input_data %>% filter(Site == "CA-DBB") #all data separated by site
CA_DB2 <- Env.input_data %>% filter(Site == "CA-DB2")
```

## {.tabset .tabset-fade}

### Environmental variables

__Air temperature__

```{r Air temperature, fig.width=10, fig.height=4}
Ta.p <- ggplot(Env.input_data, aes(x = as.Date(jday, origin = as.Date("2020-01-01")), Ta_mean)) + #as.Date adds the month names into the plot
  #geom_ribbon(aes(ymin = Ta_min -1 , ymax = Ta_max+1), fill = "light grey")+
    geom_line(aes (color=Site)) +
   ylab("Air temperature (deg C)")+
  xlab("Month") +
   #ggtitle("Air temperature at BB1 and BB2")+
   scale_x_date(date_breaks = "1 month", date_labels = "%b") +
   scale_color_aaas()+
  theme_bw()+
  theme(axis.text = element_text(size=8),
    axis.title.x=element_blank(),
        #axis.text.x=element_blank(),
        #axis.ticks.x=element_blank(),
    legend.position = "none")
ggplotly(Ta.p)

t.test(Ta_mean~Site, data = Env.input_data)

Env.input_data %>% group_by(Site, Period) %>%
  summarise(mean(Ta_mean))

shapiro.test(Env.input_data$Ta_mean)
```

```{r VPD, fig.width=10, fig.height=4}
(VPD.p <- ggplot(Env.input_data, aes(x = as.Date(jday, origin = as.Date("2020-01-01")), VPD_mean)) + #as.Date adds the month names into the plot
  #geom_ribbon(aes(ymin = Ta_min -1 , ymax = Ta_max+1), fill = "light grey")+
    geom_line(aes (color=Site)) +
   ylab("Vapor pressure \ndeficit (kPa)")+
  xlab("Month") +
   scale_x_date(date_breaks = "1 month", date_labels = "%b") +
   scale_color_jco()+
  theme_bw()+
   ggtitle ("c")+
  theme(axis.text = element_text(size=13),
        axis.title = element_text(size=14),
    #axis.title.x=element_blank(),
     #   axis.text.x=element_blank(),
      #  axis.ticks.x=element_blank(),
    legend.position = "none"))

kruskal.test(VPD_mean~Site, data = Env.input_data)

Env.input_data %>% group_by(Site) %>%
  summarise(mean(VPD_mean))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/VPD.tiff", width = 7, height = 4, device='tiff', dpi=300)

```

__Relative humidity__

```{r Relative humidity, fig.width=10, fig.height=4}
RH.p <- ggplot(Env.input_data, aes(x = as.Date(jday, origin = as.Date("2020-01-01")), RH_mean)) + #as.Date adds the month names into the plot
  #geom_ribbon(aes(ymin = RH_min -1 , ymax = RH_max +1), fill = "light grey")+
    geom_line(aes (color=Site)) +
   ylab("Relative humidity (%)")+
  xlab("Month") +
   #ggtitle("Air temperature at BB1 and BB2")+
   scale_x_date(date_breaks = "1 month", date_labels = "%b") +
   scale_color_aaas()+
  theme_bw() +
  theme(axis.text = element_text(size=8),
    axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        legend.position = "none")
ggplotly(RH.p)

kruskal.test(RH_mean~Site, data = Env.input_data)

Env.input_data %>% group_by(Site, Period) %>%
  summarise(mean(RH_mean))
```

__Water table height__

```{r Water table height, fig.width=10, fig.height=4}
(WTH.p <- ggplot(Env.input_data, aes(x = as.Date(jday, origin = as.Date("2020-01-01")), WTH._mean)) + #as.Date adds the month names into the plot
  #geom_ribbon(aes(ymin = WTH._min -1 , ymax = WTH._max+1), fill = "light grey")+
    geom_line(aes (color=Site)) +
   ylab("Water table \nheight (cm)")+
  xlab("Month") +
   ggtitle("b")+
   scale_x_date(date_breaks = "1 month", date_labels = "%b") +
          #scale_color_viridis(discrete = "TRUE", option = "D", begin = 0, end = 0.5)+
   scale_color_jco()+
  theme_bw() +
  theme(axis.text = element_text(size=14),
        axis.title = element_text(size=15),
        #legend.title = element_text(size = 15),
        #legend.text = element_text(size = 15),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        legend.position = "none"))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/WTH.tiff", width = 7, height = 4, device='tiff', dpi=300)


# to fill WTH gaps: linearly interpolate (BB1)
BB1.WTH <- Env.input_data %>% dplyr::select(Site, jday, WTH._mean)
BB1.WTH <- BB1.WTH %>% filter(Site == "CA-DBB")
ApproxFun <- approxfun(x = BB1.WTH$jday, y = BB1.WTH$WTH._mean)
Dates <- seq(1, 366, by = 1)
LinearFit <- ApproxFun(Dates)
BB1 <- as.numeric(LinearFit)
BB1.linear <- as.data.frame(BB1)

Env.input_data$WTH._mean<- ifelse(Env.input_data$Site == 'CA-DBB', NA, Env.input_data$WTH._mean)
Env.input_data$WTH._mean[which(is.na(Env.input_data$WTH._mean))] = BB1.linear$BB1


t.test(WTH._mean~Site, data = Env.input_data)

Env.input_data %>% group_by(Site, Period) %>%
  summarise(min(WTH._mean, na.rm = TRUE))
```

__5cm soil temperature__

```{r T5cm Soil temperature, fig.width=10, fig.height=4}
(TS.5.p <- ggplot(Env.input_data, aes(x = as.Date(jday, origin = as.Date("2020-01-01")), TS.5_mean)) + #as.Date adds the month names into the plot
  #geom_ribbon(aes(ymin = TS.5_min -1 , ymax = TS.5_max+1), fill = "light grey")+
    geom_line(aes (color=Site)) +
  ylab("5cm soil \ntemperature (°C)")+
  xlab("Month") +
   ggtitle("a")+
   scale_x_date(date_breaks = "1 month", date_labels = "%b") +
   scale_color_jco()+
       #scale_color_viridis(discrete = "TRUE", option = "D", begin = 0, end = 0.5)+
  theme_bw()+
  theme(legend.key.size = unit(1.5,"line"),
        axis.title = element_text(size=15),
        axis.text = element_text(size=14),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        legend.text = element_text(size =13),
      legend.title = element_text(size = 13),
       legend.position=c(0.1, 0.81)))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/TS5.tiff", width = 7, height = 4, device='tiff', dpi=300)

Env.input_data$TS.5_mean <- ifelse(Env.input_data$TS.5_mean<0, NA, Env.input_data$TS.5_mean)

# to fill TS.5 gaps: linearly interpolate (BB1)
BB1.TS5 <- Env.input_data %>% dplyr::select(Site, jday, TS.5_mean) %>%
 filter(Site == "CA-DBB")

ApproxFun <- approxfun(x = BB1.TS5$jday, y = BB1.TS5$TS.5_mean)
Dates <- seq(1, 366, by = 1)
LinearFit <- ApproxFun(Dates)
BB1 <- as.numeric(LinearFit)
BB1.linear <- as.data.frame(BB1)

Env.input_data$TS.5_mean<- ifelse(Env.input_data$Site == 'CA-DBB', NA, Env.input_data$TS.5_mean)
Env.input_data$TS.5_mean[which(is.na(Env.input_data$TS.5_mean))] = BB1.linear$BB1

# to fill TS.5 gaps: linearly interpolate (BB2)
BB2.TS5 <- Env.input_data %>% select(Site, jday, TS.5_mean) %>%
 filter(Site == "CA-DB2")

ApproxFun <- approxfun(x = BB2.TS5$jday, y = BB2.TS5$TS.5_mean)
Dates <- seq(1, 366, by = 1)
LinearFit <- ApproxFun(Dates)
BB2 <- as.numeric(LinearFit)
BB2.linear <- as.data.frame(BB2)

Env.input_data$TS.5_mean<- ifelse(Env.input_data$Site == 'CA-DB2', NA, Env.input_data$TS.5_mean)
Env.input_data$TS.5_mean[which(is.na(Env.input_data$TS.5_mean))] = BB2.linear$BB2


kruskal.test(TS.5_mean~Site, data = Env.input_data)

Env.input_data %>% group_by(Site, Period) %>%
  summarise(mean(TS.5_mean, na.rm = TRUE))


TS5WTH <- ggarrange(TS.5.p, WTH.p, VPD.p, nrow=3, common.legend = TRUE, align = "v", heights = c(1.05,1.1, 1.2))
TS5WTH

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/TS5WTH.jpeg", width = 10, height = 7, device='jpeg', dpi=300)

```

__10cm soil temperature__ - not using

```{r T10cm Soil temperature, fig.width=10, fig.height=4}
TS.10.p <- ggplot(Env.input_data, aes(x = as.Date(jday, origin = as.Date("2020-01-01")), TS.10_mean)) + #as.Date adds the month names into the plot
  #geom_ribbon(aes(ymin = TS.5_min -1 , ymax = TS.5_max+1), fill = "light grey")+
    geom_line(aes (color=Site)) +
   ylab("10cm soil temperature (deg C)")+
  xlab("Month") +
   #ggtitle("Air temperature at BB1 and BB2")+
   scale_x_date(date_breaks = "1 month", date_labels = "%b") +
   scale_color_aaas()+
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        legend.position = "none")
ggplotly(TS.10.p)
 
Env.input_data$TS.10_mean <- ifelse(Env.input_data$TS.10_mean<0, NA, Env.input_data$TS.10_mean)

# to fill TS.10 gaps: linearly interpolate (BB1)
BB1.TS10 <- Env.input_data %>% select(Site, jday, TS.10_mean) %>%
 filter(Site == "CA-DBB")

ApproxFun <- approxfun(x = BB1.TS10$jday, y = BB1.TS10$TS.10_mean)
Dates <- seq(1, 366, by = 1)
LinearFit <- ApproxFun(Dates)
BB1 <- as.numeric(LinearFit)
BB1.linear <- as.data.frame(BB1)

Env.input_data$TS.10_mean<- ifelse(Env.input_data$Site == 'CA-DBB', NA, Env.input_data$TS.10_mean)
Env.input_data$TS.10_mean[which(is.na(Env.input_data$TS.10_mean))] = BB1.linear$BB1

# to fill TS.10 gaps: linearly interpolate (BB2)
BB2.TS10 <- Env.input_data %>% select(Site, jday, TS.10_mean) %>%
 filter(Site == "CA-DB2")

ApproxFun <- approxfun(x = BB2.TS10$jday, y = BB2.TS10$TS.10_mean)
Dates <- seq(1, 366, by = 1)
LinearFit <- ApproxFun(Dates)
BB2 <- as.numeric(LinearFit)
BB2.linear <- as.data.frame(BB2)

Env.input_data$TS.10_mean<- ifelse(Env.input_data$Site == 'CA-DB2', NA, Env.input_data$TS.10_mean)
Env.input_data$TS.10_mean[which(is.na(Env.input_data$TS.10_mean))] = BB2.linear$BB2


kruskal.test(TS.10_mean~Site, data = Env.input_data)

Env.input_data %>% group_by(Site, Period) %>%
  summarise(mean(TS.10_mean, na.rm = TRUE))
```

__Precipitation__

Notes:
- 10 year average data presented below

```{r Precipitation}
library(reshape2)
#Load Environment Canada precipitation data and re-format:
EC_precip <- read.csv('/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/data/EC_precip2021.csv') 
#EC_precip$Timestamp <- as.POSIXlt(EC_precip$Timestamp, format = "%Y-%m-%d")
#EC_precip$month <- months(EC_precip$Timestamp, abbreviate = TRUE)
#EC_precip <- EC_precip %>%
 #  select(c(month, jday, Site, Precip_mean)) %>%
  #group_by(month) %>%
  #mutate(Cumsum = cumsum(Precip_mean))


#cs <- cumsum(x)
#cs[miss] <- NA
#Precip data frame has the daily total
Precip <- read.csv('/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/BBPCT.csv') 
miss <- is.na(Precip)
Precip[miss] <- 0
Precip$Time..PST. <- as.POSIXlt(Precip$Time..PST., format = "%Y-%m-%d")
Precip$month <- months(Precip$Time..PST., abbreviate = TRUE)
Precip$year <- year(Precip$Time..PST.)
Precip$jday <-yday(Precip$Time..PST.)
Precip <- Precip %>% filter(year == '2020')
Precip.cumsum <- Precip %>% group_by(month) %>%
  mutate(BB1 = cumsum(Precipitation..1.00m.),
         BB2 = cumsum(BB2.Precipitation..1.00m.))
Precip.cumsum <- Precip.cumsum %>% select(month, jday, BB1, BB2) %>%
  melt(id.vars = c("month", "jday"),
       variable.name = "Site",
       value.name = "Cumsum.Precip")

names(Precip)[2] <- "BB1"
names(Precip)[3] <-"BB2"

#Precip.2 df has the daily average rainfall, therefore it needs to be multiplied by 48(measurements taken every 30 mins)
Precip.2 <- Precip %>% select(c(month, jday, BB1, BB2))%>%
  melt(id.vars = c("month", "jday"),
       variable.name = "Site",
       value.name = "Precip")

Precip.2 <- Precip.2 %>% 
  ddply(c("Site", "month", "jday"), summarize,
        Precip_mean = (mean(Precip)*48)) %>%
  group_by(Site, month) %>%
  mutate(Cumsum = cumsum(Precip_mean))

ind.GS <- (Precip.2$jday >= 92 & Precip.2$jday <= 274)
ind.NGS <- (Precip.2$jday < 92 | Precip.2$jday >=275)

Precip.2$Period <- ''
Precip.2$Period[ind.GS] <- 'GS'
Precip.2$Period[ind.NGS] <- 'NGS'

Precip.2$Site <- revalue(Precip.2$Site, c("BB1"="CA-DBB", "BB2"="CA-DB2", "EC" = "ECCC")) #rename factors

Precip.3 <- Precip.2 %>%
  full_join(., EC_precip) %>%
  group_by(Site, month)

P.p2 <- ggplot(Precip.3, aes(month, Cumsum, fill = Site)) + 
  geom_col(position = 'dodge') +
   scale_x_discrete(limits = month.abb) +
  ylab("Precipitaion (mm)")+
   scale_fill_aaas()+
  theme_bw()
ggplotly(P.p2)

Precip.3 %>% group_by(Site) %>% summarise(sum(Precip_mean))

ind.GS.P <- (Precip.3$month == 'Apr' | Precip.3$month == 'May'|Precip.3$month == 'Jun'|Precip.3$month == 'Jul'|Precip.3$month == 'Aug'|Precip.3$month == 'Sep')
ind.NGS.P <- (Precip.3$month == 'Oct' | Precip.3$month == 'Nov'|Precip.3$month == 'Dec'|Precip.3$month == 'Jan'|Precip.3$month == 'Feb'|Precip.3$month == 'Mar')

Precip.3$Period <- ''
Precip.3$Period[ind.GS.P] <- 'GS'
Precip.3$Period[ind.NGS.P] <- 'NGS'

Precip.3 %>% group_by(Site, Period) %>% summarise(sum(Precip_mean))

kruskal.test(Cumsum~Site, data = Precip.2)
```


__SW in__
 - just using BB2

```{r Incoming SW radiation, fig.width=10, fig.height=4}
(SWin.p <- Env.input_data  %>%
   filter(Site == "CA-DB2") %>%
   ggplot(., aes(x = as.Date(jday, origin = as.Date("2020-01-01")), SWin_mean)) + 
  geom_line() +
  ylab(bquote('Incoming SW raditation (W' ~m^-2~ day^-1*')'))+
  xlab("Month")+
     scale_x_date(date_breaks = "1 month", date_labels = "%b") +
   scale_color_jco()+
  theme_bw()+
  theme(axis.text = element_text(size=14),
        axis.title = element_text(size=15),
        legend.position = "none"))

Env.input_data %>%
  summarise(mean(SWin_mean))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/SWin.tiff", width = 7, height = 4, device='tiff', dpi=300)

```


__PAR__

just using BB2 

```{r PARin, fig.width=10, fig.height=4, message=FALSE, warning = FALSE}
Parin <- read.csv('/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/met_corrected_gapfilledBB2.csv') %>% filter(DATE >= '2020-01-01 00:00:00' & DATE <'2021-01-01 00:00:00') %>%
  dplyr::select(DATE, jday, INCOMING_PAR)
Parin$DATE <- as.POSIXct(Parin$DATE, format = "%Y-%m-%d %H:%M:%S", tz="UTC")
Parin$TIME <- format(Parin$DATE, format = "%H:%M:%S", tz="UTC")
Parin$month <- months(Parin$DATE, abbreviate = TRUE)


ind.GS <- (Parin$jday >= 92 & Parin$jday <= 274)
ind.NGS <- (Parin$jday < 92 | Parin$jday >=275)

Parin$Period <- " "
Parin$Period[ind.GS] <- "GS"
Parin$Period[ind.NGS] <- "NGS"

Parin.2<- Parin %>% mutate(Parin.30 = INCOMING_PAR*1800) %>%
  group_by(jday) %>%
  mutate(Parin.daily = cumsum(Parin.30)) %>%
  mutate(Parcum.mol = Parin.daily/1000000)


Daily.Par <- Parin.2 %>%
  group_by(jday) %>%
  summarise_all(last)
#Daily.Par <- Daily.Par[-c(68),]


Monthly.Par <- Daily.Par %>%
  group_by(month) %>% mutate(
    Parin.cumsum.month =cumsum(Parcum.mol)) %>%
  arrange(month) %>%
  group_by(month) %>%
  summarise_all(last)

Monthly.Par$month <- as.factor(Monthly.Par$month)

Monthly.Par %>% group_by(Period) %>% summarise(sum(Parin.cumsum.month))
  
(Parin.p <- Daily.Par %>%
   ggplot(., aes(x = as.Date(jday, origin = as.Date("2020-01-01")), Parcum.mol)) + 
  geom_line(aes(color = "Parcum.mol")) +
    ylab(bquote('Incoming PAR (mol'~m^-2~day^-1*')'))+
  xlab("Month")+
    ggtitle("b") +
     scale_x_date(date_breaks = "1 month", date_labels = "%b") +
   scale_color_jco()+
  theme_bw()+
  theme(axis.text = element_text(size=14),
        axis.title = element_text(size=15),
        legend.position = "none"))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/PARin.tiff", width = 7, height = 4, device='tiff', dpi=300)


(PAR.p <- 
  ggplot(Monthly.Par, aes(month, Parin.cumsum.month)) + 
  geom_col(position = 'dodge', aes(fill = "Parin.cumsum.month")) +
   scale_x_discrete(limits = month.abb) +
  ylab(bquote('Incoming PAR ( mol'  ~m^-2~month^-1*')'))+
    xlab("Month")+
    ggtitle("b")+
   scale_fill_jco()+
    #scale_fill_manual(values = "#0073C2FF")+
  theme_bw()+
  theme(axis.text = element_text(size = 14),
        axis.title = element_text(size=15),
       # axis.text.x = element_blank(),
      #axis.title.x = element_blank(),
      legend.position = "none"))


ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/PARinbar.tiff", width = 7, height = 4, device='tiff', dpi=300)


```

__NDVI__

Notes: 
- Checked both a lienar and a spline fit - spline fit filled til the end of the year at seemed to fit the data better so going to go with that. Maybe should use linear? 
- Going to go with linear fit...

```{r load NDVI data and gap fill, figures-side, fig.show="hold", out.width="50%"}
library(zoo)
NDVI1 <- read.csv('/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB_ndvi/bb1_ndvi.csv')
NDVI1$Site <- 'CA-DBB'
ind <- which(NDVI1$system.time_start == '13-Jul-20')
NDVI1$NDVI[ind] <- NA
NDVI2 <- read.csv('/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB_ndvi/bb2_ndvi.csv')  
NDVI2$Site <- 'CA-DB2'
NDVI <- full_join(NDVI1, NDVI2)
NDVI$DATE <- dmy(NDVI$system.time_start)

NDVI$jday <- yday(NDVI$DATE)
NDVI <- NDVI %>%
  dplyr::select(c(jday, Site, NDVI, DATE))


(NDVI.p <- ggplot(NDVI, aes(DATE, NDVI)) + 
  geom_line(aes (color = Site)) +
    scale_x_date(date_breaks = "2 weeks") +
   scale_color_jco()+
  theme_bw()+ 
    theme(axis.text.x = element_text(angle = 90)))

CADBB.NDVI <- NDVI %>% filter(Site == "CA-DBB") %>% dplyr::select(DATE, NDVI, Site)
CADBB.NDVI$jday <- yday(CADBB.NDVI$DATE)
ApproxFun <- approxfun(x = CADBB.NDVI$DATE, y = CADBB.NDVI$NDVI)
Dates <- seq.Date(ymd("2020-01-01"), ymd("2020-12-31"), by = 1)
#Dates <- seq(1, 366, by = 1)

LinearFit <- ApproxFun(Dates)
CADBB <- as.numeric(LinearFit)
CADBB.linear <- as.data.frame(CADBB)
CADBB.linear$Site <- "CA-DBB"
CADBB.linear$jday <- c(1:366)
names(CADBB.linear)[1] <- "LinearFit"

SplineFun <- splinefun(x = CADBB.NDVI$DATE, y = CADBB.NDVI$NDVI, method = "natural")
SplineFit <- SplineFun(Dates)
#summary(SplineFit) #Use spline fit I think to gapfill
CADBB <- as.numeric(SplineFit)
CADBB.spline <- as.data.frame(CADBB)     # use spline because it does the whole year                
CADBB.spline$Site <- "CA-DBB"
CADBB.spline$jday <- c(1:366)
names(CADBB.spline)[1] <- "SplineFit"

plot(CADBB.NDVI$DATE, y = CADBB.NDVI$NDVI, ylim = c(0.3, 0.8))
lines(Dates, SplineFit, col = "red")
lines(Dates, LinearFit, col = "blue")   

CADB2.NDVI <- NDVI %>% filter(Site == "CA-DB2") %>% dplyr::select(DATE, NDVI, Site)
CADB2.NDVI$jday <- yday(CADB2.NDVI$DATE)

ApproxFun <- approxfun(x = CADB2.NDVI$DATE, y = CADB2.NDVI$NDVI)
#Dates <- seq.Date(ymd("2020-01-01"), ymd("2020-12-31"), by = 1)
LinearFit <- ApproxFun(Dates)
CADB2 <- as.numeric(LinearFit)
CADB2.linear <- as.data.frame(CADB2)
CADB2.linear$Site <- "CA-DB2"
CADB2.linear$jday <- c(1:366)
names(CADB2.linear)[1] <- "LinearFit"

SplineFun <- splinefun(x = CADB2.NDVI$DATE, y = CADB2.NDVI$NDVI, method = "natural")
SplineFit <- SplineFun(Dates)
CADB2 <- as.numeric(SplineFit)
CADB2.spline <-as.data.frame(SplineFit)
CADB2.spline$Site <- "CA-DB2"
CADB2.spline$jday <- c(1:366)

plot(CADB2.NDVI$DATE, y = CADB2.NDVI$NDVI, ylim = c(0.3, 0.8))
lines(Dates, SplineFit, col = "red")
lines(Dates, LinearFit, col = "blue") 

NDVI.new <- full_join(CADBB.linear, CADB2.linear)
names(NDVI.new)[1] <- "NDVI_lf"

Env.input_data <- full_join(Env.input_data, NDVI.new)
```

```{r NDVI}
ind.GS <- (NDVI.new$jday >= 92 & NDVI.new$jday <= 274)
ind.NGS <- (NDVI.new$jday < 92 | NDVI.new$jday >=275)

NDVI.new$Period <- " "
NDVI.new$Period[ind.GS] <- "GS"
NDVI.new$Period[ind.NGS] <- "NGS"

NDVI.GS <- NDVI.new %>% filter(Period == "GS")
NDVI.NGS <- NDVI.new %>% filter(Period == "NGS")


(NDVI.p <- ggplot(NDVI.new, aes(x = as.Date(jday, origin = as.Date("2020-01-01")), NDVI_lf)) + 
 geom_line(aes(colour = Site)) +
  ylab("NDVI")+
  xlab("Month") +
   ggtitle("b") +
    scale_x_date(date_breaks = "1 month", date_labels = "%b") +
   scale_color_jco()+
  theme_bw()+
  theme(axis.text = element_text(size=14),
        axis.title = element_text(size=15),
        legend.text = element_text(size =13),
      legend.title = element_text(size = 13),
       legend.position=c(0.15, 0.86),
      axis.title.x = element_blank(),
      axis.text.x = element_blank()))

NDVI.sum <- NDVI.new %>% group_by(Site, Period) %>%
  summarise(mean(NDVI_lf, na.rm = TRUE))

kruskal.test(NDVI_lf~Site, data = NDVI.new)

aov.NDVI <- aov(NDVI_lf~Site*Period, data = NDVI.new)
summary(aov.NDVI)
TukeyHSD(aov.NDVI)

##playing around to predict NDVI from GPP


ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/NDVI.tiff", width = 7, height = 4, device='tiff', dpi=300)

(ParNDVI <- ggarrange(NDVI.p,Parin.p, nrow = 2, common.legend = TRUE,align = "v", heights = c(1, 1.2)))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/PARNDVI.tiff", width = 10, height = 7, device='tiff', dpi=330)

```


__Compare to nearby weather station (Burns Bog) 10 year average data (from Env. Canada)__

 - Wetter than the 10 year average in 2020
 
 - need to create table that shows how much BB average monthly temperature and rainfall deviate from EC 10 year average

```{r compre env Can 10 year average to 2020 BB, fig.width=10, fig.height=4}
EC.avg <- read.csv('/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/EC_precip/EC_climate.csv') #10 years of Env.Can data from 2011-2020

EC.avg$Timestamp <- as.POSIXct(EC.avg$Timestamp, format = "%Y-%m-%d")
EC.avg$jday <- yday(EC.avg$Timestamp)

EC.temp.avg <- EC.avg %>% dplyr::select(jday, Month, Temp) %>%
  ddply(c("jday", "Month"), summarise,
        Ta_mean = mean(Temp, na.rm = TRUE)) 
EC.temp.avg$Site <- "EC"
names(EC.temp.avg)[2] <- "month"
EC.temp.avg$month <-month.abb[EC.temp.avg$month]

Temp.avg <- Env.input_data %>% select(Site, jday, Ta_mean, month) %>%
  full_join(EC.temp.avg)
Temp.avg$Site <- revalue(Temp.avg$Site, c("EC"="ECCC", "CADBB" = "CA-DBB", "CADB2" = "CA-DB2")) #rename factors

ind.GS <- (Temp.avg$jday >= 92 & Temp.avg$jday <= 274)
ind.NGS <- (Temp.avg$jday < 92 | Temp.avg$jday >=275)

Temp.avg$Period <- ''
Temp.avg$Period[ind.GS] <- 'GS'
Temp.avg$Period[ind.NGS] <- 'NGS'

Temp.avg %>% filter(Site =="ECCC" & Period =="NGS") %>%
  summarise(mean(Ta_mean))


(Ta.p <- ggplot(Temp.avg, aes(x = as.Date(jday, origin = as.Date("2020-01-01")), Ta_mean)) + 
 geom_line(aes(colour = Site)) +
  ylab("Air temperature (°C)")+
  xlab("Month") +
  ggtitle("a") +
   scale_color_jco()+
         scale_x_date(date_breaks = "1 month", date_labels = "%b") +
  theme_bw()+
theme(legend.key.size = unit(1.5,"line"),
      axis.text = element_text(size=14),
      axis.title = element_text(size=15),
      #axis.text.x = element_blank(),
      axis.title.x = element_blank(),
     # legend.justification=c(1.25, -2),
      legend.position=c(0.18, 0.77),
      legend.text = element_text(size =13),
      legend.title = element_text(size = 13))) 

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/TAECCC.tiff", width = 7, height = 4, device='tiff', dpi=300)


EC.Precip.avg <- EC.avg %>% dplyr::select(jday, Month, Precip) %>%
  ddply(c("jday", "Month"), summarise,
       Precip_mean = mean(Precip, na.rm = TRUE)) %>%
  group_by(Month) %>%
  mutate(Precip_cumsum = cumsum(Precip_mean))

names(EC.Precip.avg)[2] <- "month"
names(EC.Precip.avg)[4] <- "Cumsum"
EC.Precip.avg$Site <- "EC"
EC.Precip.avg$month <-month.abb[EC.Precip.avg$month]

ind.GS <- (EC.Precip.avg$jday >= 92 & EC.Precip.avg$jday <= 274)
ind.NGS <- (EC.Precip.avg$jday < 92 | EC.Precip.avg$jday >=275)

EC.Precip.avg$Period <- ''
EC.Precip.avg$Period[ind.GS] <- 'GS'
EC.Precip.avg$Period[ind.NGS] <- 'NGS'


Precip.avg <- Precip.2 %>% select(Site, jday, Cumsum, Precip_mean, month, Period) %>%
  full_join(EC.Precip.avg)
Precip.avg$Site <- revalue(Precip.avg$Site, c("EC" = "ECCC")) #rename factors
Precip.avg <- Precip.avg %>% filter(Site == "CA-DB2" | Site == "ECCC") #Select only BB2 and ECCC
Precip.avg %>% group_by(Site, Period) %>% summarise(sum(Precip_mean)) 


(Precip.p <- 
  ggplot(Precip.avg, aes(month, Cumsum, fill = Site)) + 
  geom_col(position = 'dodge') +
   scale_x_discrete(limits = month.abb) +
  ylab("Precipitaion (mm)")+
    xlab("Month")+
    ggtitle("b")+
   #scale_fill_jco()+
    scale_fill_manual(values = c("CA-DB2" = "#0073C2FF", "ECCC"= "#868686FF"))+
  theme_bw()+
  theme(axis.text = element_text(size = 14),
        axis.title = element_text(size=15),
       # axis.text.x = element_blank(),
      #axis.title.x = element_blank(),
      legend.position = "none"))

aov.2 <- aov(Cumsum~Site*month, data = Precip.avg)
summary(aov.2)
TukeyHSD(aov.2)


Temp.avg.month <- Temp.avg %>% select(month, Ta_mean, Site) %>%
  ddply(c("Site", "month"), summarise,
       Temp_mean = mean(Ta_mean, na.rm = TRUE),
       sd = sd(Ta_mean, na.rm = TRUE))


ind.GS <- (Temp.avg.month$month == "Apr" |Temp.avg.month$month == "May"|Temp.avg.month$month == "Jun"|Temp.avg.month$month == "Jul"|Temp.avg.month$month == "Aug"|Temp.avg.month$month == "Sep")
ind.NGS <- (Temp.avg.month$jday < 92 | Temp.avg.month$jday >=275)

Temp.avg.month$Period <- ''
Temp.avg.month$Period[ind.GS] <- 'GS'
Precip.3$Period[ind.NGS.P] <- 'NGS'


(Temp.all.p <-
  ggplot(Temp.avg.month, aes(month, Temp_mean, fill = Site)) + 
  geom_bar(stat = "identity", position = 'dodge') +
    geom_errorbar(aes(x=month, ymin=Temp_mean-sd, ymax=Temp_mean+sd), position = "dodge")+
   scale_x_discrete(limits = month.abb) +
  #ylab("Precipitaion (mm)")+
   # xlab("Month")+
    #ggtitle("b")+
   #scale_fill_jco()+
    scale_fill_manual(values = c("CA-DB2" = "#0073C2FF", "ECCC"= "#868686FF", "CA-DBB" = "#EFC000FF"))+
  theme_bw()+
  theme(axis.text = element_text(size = 14),
        axis.title = element_text(size=15)))
       # axis.text.x = element_blank(),
      #axis.title.x = element_blank(),
      #legend.position = "none"))

#aov.1 <- aov(Temp_mean~Site*month, data = Temp.avg.all)
#summary(aov.1)
#options(max.print = 10000)
#TukeyHSD(aov.1)

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/precipECCC.tiff", width = 7, height = 4, device='tiff', dpi=300)

(TAandPrecip <- ggarrange(Ta.p, Precip.p, nrow = 2, common.legend = TRUE, align = "v", heights=c(1, 1.2)))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/precipTA.jpeg", width = 10, height = 7, device='jpeg', dpi=330)

```

```{r FIGURE: combining env data plots}
library(gridExtra)
library(cowplot)

#To create shared legend:
# Create plot with legend
legend <- ggplot(Precip.avg, aes(month, Cumsum, fill = Site)) + 
  geom_col(position = 'dodge') +
   scale_x_discrete(limits = month.abb) +
  ylab("Precipitaion (mm)")+
   scale_fill_aaas()+
  theme_bw() +
  theme(legend.position = "bottom",
        legend.title = element_text(size = 10),
  legend.text = element_text(size = 8),
  legend.key.width  =  unit(1, "lines"))+
  scale_size_area(max_size = 3)

# Create user-defined function, which extracts legends from ggplots
extract_legend <- function(my_legend) {
  step1 <- ggplot_gtable(ggplot_build(my_legend))
  step2 <- which(sapply(step1$grobs, function(x) x$name) == "guide-box")
  step3 <- step1$grobs[[step2]]
  return(step3)
}

# Apply user-defined function to extract legend
shared_legend <- extract_legend(legend)

grid.arrange(Ta.p, Precip.p, RH.p, TS.5.p, WTH.p,shared_legend, nrow = 3, ncol = 2)

grid.arrange(Ta.p, Precip.p, shared_legend, nrow = 3)


library(grid)
#To combine and save plots (run all together): 
jpeg(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/TaTs.jpeg", width =880, height = 300) # The height of the plot in inches
grid.draw(cbind(ggplotGrob(Ta.p), ggplotGrob(TS.5.p)))
dev.off()

jpeg(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/ParinNDVI.tiff", width =880, height = 300) # The height of the plot in inches
grid.draw(cbind(ggplotGrob(Parin.p), ggplotGrob(NDVI.p)))
dev.off()

jpeg(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/PrecipWTH.jpeg", width =880, height = 300) # The height of the plot in inches
grid.draw(cbind(ggplotGrob(Precip.p), ggplotGrob(WTH.p)))
dev.off()

```

### CO2 and CH4 balance



Fulldata <- Fulldata %>%
  mutate(CH4_gC = (ch4gC + 0.03),
         CH4_mgC = (ch4mgC + 26)) %>%
  mutate(logCH4_gC = log(CH4_gC),
         logCH4_mgC = log(CH4_mgC))

```{r read in daily mean CO2 and CH4 fluxes}
setwd(wd)

# This file has daily averaged gap filled data
Flux.input_file <- "data/flux.csv" 
Flux.input_data <- read.csv(Flux.input_file) 

Flux.ind.GS <- (Flux.input_data$jday >= 92 & Flux.input_data$jday <= 274) 
Flux.ind.NGS <-(Flux.input_data$jday < 92 | Flux.input_data$jday >=275)

Flux.input_data$Period <- " "
Flux.input_data$Period[Flux.ind.GS] <- "GS"
Flux.input_data$Period[Flux.ind.NGS] <- "NGS"

Flux.input_data$Site <- revalue(Flux.input_data$Site, c("BB1"="CA-DBB", "BB2"="CA-DB2")) #rename factors

```

```{r calculate uncertainty}
molarMass <- 12.011
##BB2
BB2unc <- read.csv('/Users/marionnyberg/Google\ Drive/Micromet\ Lab/Projects/2019-Burns\ Bog\ 2/Flux-tower/flux_data/FilledEddyData.csv') %>% dplyr::select(DateTime, NEE_U05_f, NEE_U95_f, GPP_U05_f, GPP_U95_f, Reco_U05, Reco_U95)
BB2unc$DateTime <- as.POSIXct(BB2unc$DateTime, format = "%Y-%m-%d %H:%M:%S", tz="UTC")
BB2unc <- BB2unc %>% filter (DateTime >= "2020-01-01 00:00:00"  & DateTime < "2021-01-01 00:00:00")
BB2unc$jday <- yday(BB2unc$DateTime)
BB2unc$Period <- ""
ind.GS <- (BB2unc$jday >= 92 & BB2unc$jday <= 274)
ind.NGS <- (BB2unc$jday < 92 | BB2unc$jday >=275)
BB2unc$Period[ind.GS] <- 'GS'
BB2unc$Period[ind.NGS] <- 'NGS'

#NEE
L.2 <-mean(BB2unc$NEE_U05_f) * 1e-6 * molarMass * (3600*24*365.25)
U.2 <- mean(BB2unc$NEE_U95_f) * 1e-6 *  molarMass * (3600*24*365.25)

std.2 <- (U.2 - L.2)/(2*1.645)
CI95.2 <- std.2 *1.96

CI95.2 * (44.01/12.01)

#GPP
L.2.GPP <-mean(BB2unc$GPP_U05_f) * 1e-6 * molarMass * (3600*24*365.25)
U.2.GPP <- mean(BB2unc$GPP_U95_f) * 1e-6 *  molarMass * (3600*24*365.25)

std.2.GPP <- (U.2.GPP - L.2.GPP)/(2*1.645)
CI95.2.GPP <- std.2.GPP *1.96

#RECO
L.2.RECO <-mean(BB2unc$Reco_U05) * 1e-6 * molarMass * (3600*24*365.25)
U.2.RECO <- mean(BB2unc$Reco_U95) * 1e-6 *  molarMass * (3600*24*365.25)

std.2.RECO <- (U.2.RECO - L.2.RECO)/(2*1.645)
CI95.2.RECO<- std.2.RECO *1.96

#BB2 GS
BB2unc.GS <- BB2unc %>% filter (Period == "GS")

#NEE
L.2.GS <-mean(BB2unc.GS$NEE_U05_f) * 1e-6 * molarMass * (3600*24*182)
U.2.GS <- mean(BB2unc.GS$NEE_U95_f) * 1e-6 *  molarMass * (3600*24*182)

std.2.GS <- (U.2.GS - L.2.GS)/(2*1.645)
CI95.2.GS <- std.2.GS *1.96

#GPP
L.2.GPP.GS <-mean(BB2unc.GS$GPP_U05_f) * 1e-6 * molarMass * (3600*24*182)
U.2.GPP.GS <- mean(BB2unc.GS$GPP_U95_f) * 1e-6 *  molarMass * (3600*24*182)

std.2.GPP.GS <- (U.2.GPP.GS - L.2.GPP.GS)/(2*1.645)
CI95.2.GPP.GS <- std.2.GPP.GS *1.96

#RECO
L.2.RECO.GS <-mean(BB2unc.GS$Reco_U05) * 1e-6 * molarMass * (3600*24*182)
U.2.RECO.GS <- mean(BB2unc.GS$Reco_U95) * 1e-6 *  molarMass * (3600*24*182)

std.2.RECO.GS<- (U.2.RECO.GS - L.2.RECO.GS)/(2*1.645)
CI95.2.RECO.GS <- std.2.RECO.GS *1.96


#BB2 NGS
BB2unc.NGS <- BB2unc %>% filter (Period == "NGS")

#NEE
L.2.NGS <-mean(BB2unc.NGS$NEE_U05_f) * 1e-6 * molarMass * (3600*24*184)
U.2.NGS <- mean(BB2unc.NGS$NEE_U95_f) * 1e-6 *  molarMass * (3600*24*184)

std.2.NGS <- (U.2.NGS - L.2.NGS)/(2*1.645)
CI95.2.NGS <- std.2.NGS *1.96

#GPP
L.2.GPP.NGS <-mean(BB2unc.NGS$GPP_U05_f) * 1e-6 * molarMass * (3600*24*184)
U.2.GPP.NGS <- mean(BB2unc.NGS$GPP_U95_f) * 1e-6 *  molarMass * (3600*24*184)

std.2.GPP.NGS <- (L.2.GPP.NGS - U.2.GPP.NGS)/(2*1.645)
CI95.2.GPP.NGS <- std.2.GPP.NGS *1.96

#RECO
L.2.RECO.NGS <-mean(BB2unc.NGS$Reco_U05) * 1e-6 * molarMass * (3600*24*184)
U.2.RECO.NGS <- mean(BB2unc.NGS$Reco_U95) * 1e-6 *  molarMass * (3600*24*184)

std.2.RECO.NGS<- (U.2.RECO.NGS - L.2.RECO.NGS)/(2*1.645)
CI95.2.RECO.NGS <- std.2.RECO.NGS *1.96

BB1unc <- read.csv('/Users/marionnyberg/Google\ Drive/Micromet\ Lab/Projects/2014-Burns\ Bog/Flux-tower/flux_data/FilledEddyData.csv') %>% dplyr::select(DateTime, NEE_U05_f, NEE_U95_f, GPP_U05_f, GPP_U95_f, Reco_U05, Reco_U95)
BB1unc$DATE <- as.POSIXct(BB1unc$DateTime, format = "%Y-%m-%d %H:%M:%S", tz="UTC")
BB1unc <- BB1unc %>% filter (DATE >= "2020-01-01 00:00:00"  & DATE < "2021-01-01 00:00:00")
BB1unc$jday <- yday(BB1unc$DateTime)
BB1unc$Period <- ""
ind.GS <- (BB1unc$jday >= 92 & BB1unc$jday <= 274)
ind.NGS <- (BB1unc$jday < 92 | BB1unc$jday >=275)
BB1unc$Period[ind.GS] <- 'GS'
BB1unc$Period[ind.NGS] <- 'NGS'

L.1 <-mean(BB1unc$NEE_U05_f) * 1e-6 * molarMass * (3600*24*365.25)
U.1 <- mean(BB1unc$NEE_U95_f) * 1e-6 *  molarMass * (3600*24*365.25)

std.1 <- (U.1 - L.1)/(2*1.645)
CI95.1 <- std.1 *1.96

CI95.1 * (44.01/12.01)

#GPP
L.1.GPP <-mean(BB1unc$GPP_U05_f) * 1e-6 * molarMass * (3600*24*365.25)
U.1.GPP <- mean(BB1unc$GPP_U95_f) * 1e-6 *  molarMass * (3600*24*365.25)

std.1.GPP <- (U.1.GPP - L.1.GPP)/(2*1.645)
CI95.1.GPP <- std.1.GPP *1.96

#RECO
L.1.RECO <-mean(BB1unc$Reco_U05) * 1e-6 * molarMass * (3600*24*365.25)
U.1.RECO <- mean(BB1unc$Reco_U95) * 1e-6 *  molarMass * (3600*24*365.25)

std.1.RECO <- (U.1.RECO - L.1.RECO)/(2*1.645)
CI95.1.RECO<- std.1.RECO *1.96

#BB1 GS
BB1unc.GS <- BB1unc %>% filter (Period == "GS")

#NEE
L.1.GS <-mean(BB1unc.GS$NEE_U05_f) * 1e-6 * molarMass * (3600*24*182)
U.1.GS <- mean(BB1unc.GS$NEE_U95_f) * 1e-6 *  molarMass * (3600*24*182)

std.1.GS <- (U.1.GS - L.1.GS)/(2*1.645)
CI95.1.GS <- std.1.GS *1.96

#GPP
L.1.GPP.GS <-mean(BB1unc.GS$GPP_U05_f) * 1e-6 * molarMass * (3600*24*182)
U.1.GPP.GS <- mean(BB1unc.GS$GPP_U95_f) * 1e-6 *  molarMass * (3600*24*182)

std.1.GPP.GS <- (U.1.GPP.GS - L.1.GPP.GS)/(2*1.645)
CI95.1.GPP.GS <- std.1.GPP.GS *1.96

#RECO
L.1.RECO.GS <-mean(BB1unc.GS$Reco_U05) * 1e-6 * molarMass * (3600*24*182)
U.1.RECO.GS <- mean(BB1unc.GS$Reco_U95) * 1e-6 *  molarMass * (3600*24*182)

std.1.RECO.GS<- (U.1.RECO.GS - L.1.RECO.GS)/(2*1.645)
CI95.1.RECO.GS <- std.1.RECO.GS *1.96

#BB1 NGS
BB1unc.NGS <- BB1unc %>% filter (Period == "NGS")

#NEE
L.1.NGS <-mean(BB1unc.NGS$NEE_U05_f) * 1e-6 * molarMass * (3600*24*184)
U.1.NGS <- mean(BB1unc.NGS$NEE_U95_f) * 1e-6 *  molarMass * (3600*24*184)

std.1.NGS <- (U.1.NGS - L.1.NGS)/(2*1.645)
CI95.1.NGS <- std.1.NGS *1.96

#GPP
L.1.GPP.NGS <-mean(BB1unc.NGS$GPP_U05_f) * 1e-6 * molarMass * (3600*24*184)
U.1.GPP.NGS <- mean(BB1unc.NGS$GPP_U95_f) * 1e-6 *  molarMass * (3600*24*184)

std.1.GPP.NGS <- (U.1.GPP.NGS - L.1.GPP.NGS)/(2*1.645)
CI95.1.GPP.NGS <- std.1.GPP.NGS *1.96

#RECO
L.1.RECO.NGS <-mean(BB1unc.NGS$Reco_U05) * 1e-6 * molarMass * (3600*24*184)
U.1.RECO.NGS <- mean(BB1unc.NGS$Reco_U95) * 1e-6 *  molarMass * (3600*24*184)

std.1.RECO.NGS<- (U.1.RECO.NGS - L.1.RECO.NGS)/(2*1.645)
CI95.1.RECO.NGS <- std.1.RECO.NGS *1.96

```


__Cumulative NEE__

By the end of 2020, BB1 was a CO2 sink, but BB2 was a source of CO2 to the atmosphere. Despite higher GPP at BB2, ER is also much greater, which is leading to it acting as a CO2 source. When only considering CO2, this is not an effective management strategy, or it is at a stage in it's recovery trajectory where it is a source of CO2 to the atmosphere.

- Daily mean cumulative NEE  (gC m-2 day-1)
- Using daily averages of NEEgC_f values
- CUP - how does this differ between the sites? 
- When comparing this to Nick's data from June 2015- June 2016 ~ -179 g CO2 C, the sink strength of BB1 in 2020 was -59 g CO2. This is nearly 1/3 of what is was 3 years previously. (need to look at environmental conditions)

```{r Cumulative NEE}
(NEEcum.p <-Flux.input_data %>% 
  ggplot(., aes(x = as.Date(jday, origin = as.Date("2020-01-01")), NEEcum, color = Site)) +
  geom_line(aes(color = Site))+
  ylab(bquote('Cumulative NEE (g C' ~m^-2~')'))+
  xlab("Month")+
    scale_x_date(date_breaks = "1 month", date_labels = "%b") +
   scale_color_jco()+
   ggtitle("a")+
  theme_bw()+
   theme(axis.text = element_text(size=14),
      axis.title = element_text(size=15),
      axis.title.x = element_blank(),
      axis.text.x = element_blank(),
      legend.text = element_text(size = 13),
      legend.title = element_text(size = 13),
      legend.key.size = unit(1.5, "line")))#,
      #legend.justification=c(1.25, -1.8),
                        #legend.position=c(.9, 0.2)))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/NEEcum.tiff", width = 7, height = 4, device='tiff', dpi=300)


Flux.input_data %>%
  dplyr::select(c(Site, NEEcum, jday)) %>%
  group_by(Site) %>%
  mutate(row = row_number()) %>%
  pivot_wider(names_from = Site, values_from = NEEcum)

kruskal.test(NEEcum ~ Site, data = Flux.input_data)

(NEE.time.p <-Flux.input_data %>% 
  ggplot(., aes(x = as.Date(jday, origin = as.Date("2020-01-01")), NEEgC_f, color = Site)) +
  geom_line(aes(color = Site))+
  ylab(bquote('NEE (g C' ~m^-2~ day^-1*')'))+
  xlab("Month")+
    scale_x_date(date_breaks = "1 month", date_labels = "%b") +
   scale_color_jco()+
    ggtitle("b")+
  theme_bw()+
    theme(axis.text = element_text(size=14),
      axis.title = element_text(size=15),
      legend.position = "none"))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/NEEtime.tiff", width = 7, height = 4, device='tiff', dpi=300)


Flux.input_data %>% group_by(Site, Period) %>%
  summarise(sum(NEEgC_f))

GS.Flux.input_data <- Flux.input_data %>% filter(Period == "GS")
t.test(NEEcum ~ Site, data = GS.Flux.input_data)

GS.Flux.input_data<- GS.Flux.input_data %>% group_by(Site) %>% mutate(cum.NEE2 = cumsum(NEEgC_f))

NGS.Flux.input_data <- Flux.input_data %>% filter(Period == "NGS")
kruskal.test(NEEcum ~ Site, data = GS.Flux.input_data)
kruskal.test(NEEgC_f ~ Site, NGS.Flux.input_data)


NGS.Flux.input_data<- NGS.Flux.input_data %>% group_by(Site) %>% mutate(cum.NEE2 = cumsum(NEEgC_f))

GS.Flux.input_data %>% filter(Site =="CA-DBB") %>% summarise(mean(NEE_f))
GS.Flux.input_data %>% filter(Site =="CA-DB2") %>% summarise(mean(NEE_f))

NGS.Flux.input_data %>% filter(Site =="CA-DBB") %>% summarise(mean(NEE_f))
NGS.Flux.input_data %>% filter(Site =="CA-DB2") %>% summarise(mean(NEE_f))

NEE.arranged <- ggarrange(NEEcum.p, NEE.time.p, nrow = 2, common.legend = TRUE, align = "v", heights=c(1, 1.2))
NEE.arranged

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/NEEarranged.tiff", width = 9, height = 7, device='tiff', dpi=330)

```



__Cumulative GPP__

```{r Cumulative and timeseries GPP}
(GPPcum.p <-Flux.input_data %>% 
  ggplot(., aes(x = as.Date(jday, origin = as.Date("2020-01-01")), GPPcum_f, color = Site)) +
  geom_line()+
  ylab(bquote('Cumulative GPP (g C' ~m^-2~')'))+
  xlab("Month")+
   ggtitle("a") +
     scale_x_date(date_breaks = "1 month", date_labels = "%b") +
    scale_color_jco()+
  theme_bw()+
    theme(axis.text = element_text(size=14),
      axis.title = element_text(size=15),
      axis.title.x=element_blank(),
        axis.text.x=element_blank(),
      legend.key.size = unit(1.5, "line"),
      legend.text = element_text(size = 13),
      legend.title = element_text(size = 13),
                        legend.position=c(.15, 0.8)))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/GPPcum.tiff", width = 7, height = 4, device='tiff', dpi=300)


Flux.input_data %>%
  dplyr::select(c(Site, GPPcum_f, jday)) %>%
  group_by(Site) %>%
  mutate(row = row_number()) %>%
  pivot_wider(names_from = Site, values_from = GPPcum_f) %>%
  summarise(BB1 = last(na.omit(BB1)),
            BB2 = last(na.omit(BB2))) %>%
  kbl(caption = "Total GPP") %>%
  kable_classic(html_font = "Cambria")

kruskal.test(GPPcum_f ~ Site, data = Flux.input_data)

(GPP.p <-Flux.input_data %>% 
  ggplot(., aes(x = as.Date(jday, origin = as.Date("2020-01-01")), GPPgC_f, color = Site)) +
  geom_line()+
  ylab(bquote('GPP (g C' ~m^-2~ day^-1*')'))+
  xlab("Month")+
     scale_x_date(date_breaks = "1 month", date_labels = "%b") +
    scale_color_jco()+
    ggtitle("b")+
  theme_bw()+
    theme(axis.text = element_text(size=14),
      axis.title = element_text(size=15),
      legend.position = "none"))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/GPPtime.tiff", width = 7, height = 4, device='tiff', dpi=300)

GPP.arranged <- ggarrange(GPPcum.p, GPP.p, nrow = 2, common.legend = TRUE, align = "v", heights=c(1, 1.2))
GPP.arranged

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/GPParranged.tiff", width = 9, height = 7, device='tiff', dpi=330)

Flux.input_data %>% group_by(Site, Period) %>%
  summarise(sum(GPPgC_f))

kruskal.test(GPPcum_f ~ Site, data = GS.Flux.input_data)
kruskal.test(GPPcum_f ~ Site, data = NGS.Flux.input_data)

cumsumGPP <- Flux.input_data %>%
  dplyr::select(c(Site, GPPgC_f, jday, month_local)) %>%
  group_by(Site, month_local) %>%
  mutate(row = row_number()) %>%
  pivot_wider(names_from = Site, values_from = GPPgC_f)

new <- cumsumGPP %>% group_by(month_local) %>%
  summarise(GPPcum = cumsum(`CA-DB2`))
```


__Ecosystem respiration__

- When does Reco peak at each site? It seems to peak earlier at BB1 than BB2. Is there evidence of rhizosphere priming? Is it sustained? 

```{r Cumulative and timeseries ER}
(Recocum.p <-Flux.input_data %>% 
  ggplot(., aes(x = as.Date(jday, origin = as.Date("2020-01-01")), Recocum, color = Site)) +
  geom_line()+
  ylab(bquote('Cumulative RECO (g C' ~m^-2~')'))+
  xlab("Month")+
 scale_x_date(date_breaks = "1 month", date_labels = "%b") +
    scale_color_jco()+
   ggtitle("a")+
 theme_bw()+
    theme(axis.text = element_text(size=14),
      axis.title = element_text(size=15),
      axis.title.x = element_blank(),
      axis.text.x = element_blank(),
      legend.key.size = unit(1.5, "line"),
      legend.text = element_text(size = 13),
      legend.title = element_text(size = 13),
      legend.position=c(.15, 0.8)))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/Recocum.tiff", width = 7, height = 4, device='tiff', dpi=300)

Flux.input_data %>%
  dplyr::select(c(Site, Recocum, jday)) %>%
  group_by(Site) %>%
  mutate(row = row_number()) %>%
  pivot_wider(names_from = Site, values_from = Recocum) %>%
  summarise(BB1 = last(na.omit(BB1)),
            BB2 = last(na.omit(BB2))) %>%
  kbl(caption = "Total REco") %>%
  kable_classic(html_font = "Cambria")

kruskal.test(Recocum ~ Site, data = Flux.input_data)

(Reco.p <-Flux.input_data %>% 
  ggplot(., aes(x = as.Date(jday, origin = as.Date("2020-01-01")), RecogC, color = Site)) +
  geom_line()+
    #scale_colour_manual(values = c("#0072B2", "#D55E00")) +
  ylab(bquote('RECO (g C' ~m^-2~ day^-1*')'))+
  xlab("Month")+
 scale_x_date(date_breaks = "1 month", date_labels = "%b") +
    scale_color_jco()+
    ggtitle("b")+
 theme_bw()+
    theme(axis.text = element_text(size=14),
      axis.title = element_text(size=15),
      legend.position = "none"))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/Recotime.tiff", width = 7, height = 4, device='tiff', dpi=300)

RECO.arranged <- ggarrange(Recocum.p, Reco.p, nrow = 2, common.legend = TRUE, align = "v", heights=c(1, 1.2))
RECO.arranged

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/Recoarranged.tiff", width = 9, height = 7, device='tiff', dpi=330)

Flux.input_data %>% group_by(Site, Period) %>%
  summarise(sum(RecogC))

BB2.flux <- Flux.input_data %>% select(Site, RecogC, Period, jday) %>% filter(Site =="BB2")
BB1.flux <- Flux.input_data %>% select(Site, RecogC, Period, jday) %>% filter(Site =="BB1")

kruskal.test(Recocum ~ Site, data = GS.Flux.input_data)
kruskal.test(Recocum ~ Site, data = NGS.Flux.input_data)

```


__CH4 flux__

```{r calculate FCH4 UC}
#BB1
FCH4.UC.BB1 <- read.csv('/Users/marionnyberg/Google\ Drive/Micromet\ Lab/Projects/2014-Burns\ Bog/Flux-tower/flux_data/BB_rf_result.csv') %>% dplyr:: select (FCH4_RF_filled, DateTime, iteration) %>%
  pivot_wider(names_from = iteration, values_from = FCH4_RF_filled) 

nmolsto30 <- function(x) x*1800 
FCH4.UC.BB1.30 <- data.frame(lapply(FCH4.UC.BB1[2:21], nmolsto30))  
nmoltog <- function(x)  x * (12.01/(10^6))
FCH4.UC.BB1.g <- data.frame(lapply(FCH4.UC.BB1.30, nmoltog)) 
cumsum.F <- function(x) cumsum(x)
FCH4.UC.cumBB1 <- data.frame(lapply(FCH4.UC.BB1.30, cumsum.F)) %>% tail(n = 1)
FCH4.UC.cumBB1 <- data.frame(lapply(FCH4.UC.cumBB1, nmoltog))
FCH4.UC.cum.95BB1 <-1.96*(sd(FCH4.UC.cumBB1))

SGWPCH4.20 * (FCH4.UC.cum.95BB1 * (16.04/12.01))
SGWPCH4.100 * (FCH4.UC.cum.95BB1 * (16.04/12.01))


FCH4.UC.BB1$jday <-yday(FCH4.UC.BB1$DateTime)
FCH4.UC.BB1$Period <- ""
ind.GS <- (FCH4.UC.BB1$jday >= 92 & FCH4.UC.BB1$jday <= 274)
ind.NGS <- (FCH4.UC.BB1$jday < 92 | FCH4.UC.BB1$jday >=275)
FCH4.UC.BB1$Period[ind.GS] <- 'GS'
FCH4.UC.BB1$Period[ind.NGS] <- 'NGS'
FCH4.UC.BB1.GS <- FCH4.UC.BB1 %>% filter(Period == "GS")
FCH4.UC.BB1.NGS <- FCH4.UC.BB1 %>% filter(Period == "NGS")

FCH4.UC.BB1.30.GS <- data.frame(lapply(FCH4.UC.BB1.GS[2:21], nmolsto30))  
FCH4.UC.BB1.g.GS <- data.frame(lapply(FCH4.UC.BB1.30.GS, nmoltog)) 
FCH4.UC.cumBB1.GS <- data.frame(lapply(FCH4.UC.BB1.30.GS, cumsum.F)) %>% tail(n = 1)
FCH4.UC.cumBB1.GS <- data.frame(lapply(FCH4.UC.cumBB1.GS, nmoltog))
FCH4.UC.cum.95BB1.GS <-1.96*(sd(FCH4.UC.cumBB1.GS))

FCH4.UC.BB1.30.NGS <- data.frame(lapply(FCH4.UC.BB1.NGS[2:21], nmolsto30))  
FCH4.UC.BB1.g.NGS <- data.frame(lapply(FCH4.UC.BB1.30.NGS, nmoltog)) 
FCH4.UC.cumBB1.NGS <- data.frame(lapply(FCH4.UC.BB1.30.NGS, cumsum.F)) %>% tail(n = 1)
FCH4.UC.cumBB1.NGS <- data.frame(lapply(FCH4.UC.cumBB1.NGS, nmoltog))
FCH4.UC.cum.95BB1.NGS <-1.96*(sd(FCH4.UC.cumBB1.NGS))

#BB2
FCH4.UC.BB2 <- read.csv('/Users/marionnyberg/Google\ Drive/Micromet\ Lab/Projects/2019-Burns\ Bog\ 2/Flux-tower/flux_data/BB2_rf_result.csv') %>% dplyr:: select (FCH4_RF_filled, DateTime, iteration) %>%
  pivot_wider(names_from = iteration, values_from = FCH4_RF_filled)  %>%
  filter(DateTime >= '2020-01-01T00:30:00Z' & DateTime <= '2020-12-31T23:30:00Z') 

nmolsto30 <- function(x) x*1800 
FCH4.UC.BB2.30 <- data.frame(lapply(FCH4.UC.BB2[2:21], nmolsto30))  
nmoltog <- function(x)  x * (12.01/(10^6))
FCH4.UC.BB2.g <- data.frame(lapply(FCH4.UC.BB2.30, nmoltog)) 
cumsum.F <- function(x) cumsum(x)
FCH4.UC.cumBB2 <- data.frame(lapply(FCH4.UC.BB2.30, cumsum.F)) %>% tail(n = 1)
FCH4.UC.cumBB2 <- data.frame(lapply(FCH4.UC.cumBB2, nmoltog))
FCH4.UC.cum.95BB2 <-1.96*(sd(FCH4.UC.cumBB2))

DB2.CI95.FCH4.20 <- SGWPCH4.20 * (FCH4.UC.cum.95BB2 * (16.04/12.01))
DB2.CI95.FCH4.100 <- SGWPCH4.100 * (FCH4.UC.cum.95BB2 * (16.04/12.01))



FCH4.UC.BB2$jday <-yday(FCH4.UC.BB2$DateTime)
FCH4.UC.BB2$Period <- ""
ind.GS <- (FCH4.UC.BB2$jday >= 92 & FCH4.UC.BB2$jday <= 274)
ind.NGS <- (FCH4.UC.BB2$jday < 92 | FCH4.UC.BB2$jday >=275)
FCH4.UC.BB2$Period[ind.GS] <- 'GS'
FCH4.UC.BB2$Period[ind.NGS] <- 'NGS'
FCH4.UC.BB2.GS <- FCH4.UC.BB2 %>% filter(Period == "GS")
FCH4.UC.BB2.NGS <- FCH4.UC.BB2 %>% filter(Period == "NGS")

FCH4.UC.BB2.30.GS <- data.frame(lapply(FCH4.UC.BB2.GS[2:21], nmolsto30))  
FCH4.UC.BB2.g.GS <- data.frame(lapply(FCH4.UC.BB2.30.GS, nmoltog)) 
FCH4.UC.cumBB2.GS <- data.frame(lapply(FCH4.UC.BB2.30.GS, cumsum.F)) %>% tail(n = 1)
FCH4.UC.cumBB2.GS <- data.frame(lapply(FCH4.UC.cumBB2.GS, nmoltog))
FCH4.UC.cum.95BB2.GS <-1.96*(sd(FCH4.UC.cumBB2.GS))

FCH4.UC.BB2.30.NGS <- data.frame(lapply(FCH4.UC.BB2.NGS[2:21], nmolsto30))  
FCH4.UC.BB2.g.NGS <- data.frame(lapply(FCH4.UC.BB2.30.NGS, nmoltog)) 
FCH4.UC.cumBB2.NGS <- data.frame(lapply(FCH4.UC.BB2.30.NGS, cumsum.F)) %>% tail(n = 1)
FCH4.UC.cumBB2.NGS <- data.frame(lapply(FCH4.UC.cumBB2.NGS, nmoltog))
FCH4.UC.cum.95BB2.NGS <-1.96*(sd(FCH4.UC.cumBB2.NGS))

```

```{r calc uncertainty for radiative balance}
DB2.20.RB <- CI95.2 + DB2.CI95.FCH4.20
DB2.100.RB <- CI95.2 + DB2.CI95.FCH4.100
```

```{r CH4 flux}
test1 <- Flux.input_data %>% filter(Site == "CA-DB2") %>% mutate(FCH4BB2lower = CH4cum_f_RF_gC -27.3,
                                                                 FCH4BB2upper = CH4cum_f_RF_gC +27.3)

Flux.input_data$FCH4lowerBB2<- ifelse(Flux.input_data$Site == 'CA-DBB', NA, test1$FCH4BB2lower)
Flux.input_data$FCH4upperBB2<- ifelse(Flux.input_data$Site == 'CA-DBB', NA, test1$FCH4BB2upper)
Flux.input_data$FCH4BB2<- ifelse(Flux.input_data$Site == 'CA-DBB', NA, Flux.input_data$CH4cum_f_RF_gC)



(CH4cum.p <-Flux.input_data %>% 
  ggplot(., aes(x = as.Date(jday, origin = as.Date("2020-01-01")), CH4cum_f_RF_gC, color = Site)) +
   #geom_ribbon(aes(x = as.Date(jday, origin = as.Date("2020-01-01")), ymin = FCH4lowerBB2, ymax = FCH4upperBB2), fill = "blue", alpha = 0.25)+
  geom_line()+
    #scale_colour_manual(values = c("#0072B2", "#D55E00")) +
  ylab(bquote('Cumulative FCH4 (g C' ~m^-2~')'))+
  xlab("Month")+
     scale_x_date(date_breaks = "1 month", date_labels = "%b") +
    scale_color_jco()+
    ggtitle("a") +
  theme_bw()+
   theme(axis.text = element_text(size=14),
         axis.title = element_text(size=15),
         axis.title.x = element_blank(),
         axis.text.x = element_blank(),
         legend.position=c(.15, 0.8),
         legend.key.size = unit(1.5, "line"),
         legend.title = element_text(size = 13),
         legend.text = element_text(size= 13)))

 



  ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/CH4cum.tiff", width = 7, height = 4, device='tiff', dpi=300)


cumsumCH4 <- Flux.input_data %>%
  dplyr::select(c(Site, CH4cum_f_RF_gC, jday, month_local)) %>%
  group_by(Site, month_local) %>%
  mutate(row = row_number()) %>%
  pivot_wider(names_from = Site, values_from = CH4cum_f_RF_gC) 

cumsumCH4 <- Flux.input_data %>%
  dplyr::select(c(Site, CH4gC_f_RF, jday, month_local)) %>%
  group_by(Site, month_local) %>%
  mutate(row = row_number()) %>%
  pivot_wider(names_from = Site, values_from = CH4gC_f_RF)

new <- cumsumCH4 %>% group_by(month_local) %>%
  summarise(CH4gCcum = cumsum(`CA-DB2`))

  
  
  
  
  
  
  
  ddply(c("month_local"), summarise,
        BB1cumsum = cumsum(cumsumCH4$`CA-DBB`),
         BB2cumsum = cumsum(cumsumCH4$`CA-DB2`))
  
  



(CH4.p <-Flux.input_data %>% 
  ggplot(., aes(x = as.Date(jday, origin = as.Date("2020-01-01")), CH4mgC_f_RF, color = Site)) +
  geom_line()+
    #scale_colour_manual(values = c("#0072B2", "#D55E00")) +
  ylab(bquote('FCH4 (mg C' ~m^-2~')'))+
  xlab("Month")+
 scale_x_date(date_breaks = "1 month", date_labels = "%b") +
    scale_color_jco()+
    ggtitle("b")+
 theme_bw()+
   theme(axis.text = element_text(size=14),
         axis.title = element_text(size=15),
         legend.position = "none"))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/CH4time.tiff", width = 6, height = 4.3, device='tiff', dpi=300)

FCH4.arranged <- ggarrange(CH4cum.p, CH4.p, nrow = 2, common.legend = TRUE, align = "v", heights=c(1, 1.2))
FCH4.arranged

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/FCH4arranged.tiff", width = 9, height = 7, device='tiff', dpi=330)




CH4 <- Flux.input_data %>% select(Site, CH4mgC_f_RF, jday, Period) %>% 
  ddply(c("Site", "Period"), summarise,
        FCH4 = mean(CH4mgC_f_RF))
ch4<- aov(CH4mgC_f_RF~Site*Period, data = Flux.input_data)
TukeyHSD(ch4)

Flux.input_data %>% group_by(Site, Period) %>%
  summarise(sum(CH4gC_f_RF))

kruskal.test(CH4cum_f_RF_gC ~ Site, data = Flux.input_data)
kruskal.test(CH4cum_f_RF_gC ~ Site, data = GS.Flux.input_data)
kruskal.test(CH4cum_f_RF_gC ~ Site, data = NGS.Flux.input_data)




```

### GHG budget

```{r calculating CO2 equivalents}
#GWPCH4.20 <- 84 
#GWPCH4.100 <- 28 # no feedback
SGWPCH4.100 <- 45
SGWPCH4.20 <- 96

CO2eq <- Flux.input_data %>% 
  group_by(Site,month_local) %>%
  summarise(NEE = sum(NEEgC_f),
            CH4 = sum(CH4gC_f_RF)) %>%
  mutate(CO2_CH4eq100 = GWPCH4.100 * (CH4 * (16.04/12.01)),
         CO2_CH4eq20 = GWPCH4.20 * (CH4 * (16.04/12.01)),
         CH4_CH4 = (CH4 * (16.04/12.01)),
         CO2_CO2eq = NEE * (44.01/12.01),
         SGWP100CH4 = SGWPCH4.100 * (CH4 * (16.04/12.01)),
         SGWP20CH4 = SGWPCH4.20 * (CH4 * (16.04/12.01))) %>%
  mutate(GHG_eq100 = CO2_CH4eq100 + CO2_CO2eq,
         GHG_eq20 = CO2_CH4eq20 + CO2_CO2eq) %>%
  group_by(Site) %>%
  mutate(total.20yrGHG = cumsum(GHG_eq20),
         total.100yrGHG = cumsum(GHG_eq100),
         cumCO2 = cumsum(CO2_CO2eq),
         cumch4 = cumsum(CH4_CH4),
         cumCH420yr = cumsum(CO2_CH4eq20),
         cumCH4100yr = cumsum(CO2_CH4eq100),
         SGWPcumCH4100yr = cumsum(SGWP100CH4),
         SGWPcumCH420yr = cumsum(SGWP20CH4),
         cumCH4gC20yrSGWP = cumsum(CH4)*SGWPCH4.20,
         cumCH4gC100yrSGWP = cumsum(CH4)*SGWPCH4.100) %>%
  mutate(cumNEESGWP = cumsum(NEE) - cumsum(CH4))%>%
  mutate(cumNEECO2 = cumNEESGWP *(44.01/12.01)) %>%
  mutate(SGWPtotal20 = cumNEECO2 + cumCH4gC20yrSGWP) %>%
  mutate(SGWPtotal100 = cumNEECO2 + cumCH4gC100yrSGWP)

#USE THIS ONE BELOW
CO2eq.2 <- Flux.input_data %>% 
  group_by(Site,month_local) %>%
  summarise(NEE = sum(NEEgC_f),
            CH4 = sum(CH4gC_f_RF)) %>%
  mutate(CH4_CH4 = (CH4 * (16.04/12.01)),
         CO2_CO2eq = NEE * (44.01/12.01),
         SGWP100CH4 = SGWPCH4.100 * (CH4 * (16.04/12.01)),
         SGWP20CH4 = SGWPCH4.20 * (CH4 * (16.04/12.01))) %>%
  group_by(Site) %>%
  mutate(cumCO2 = cumsum(NEE),
         cumch4 = cumsum(CH4),
         SGWPcumCH4100yr = cumsum(SGWP100CH4),
         SGWPcumCH420yr = cumsum(SGWP20CH4)) %>%
         #cumCH4gC20yrSGWP = cumsum(CH4)*SGWPCH4.20,
         #cumCH4gC100yrSGWP = cumsum(CH4_CH4)*SGWPCH4.100) %>%
  mutate(cumNEESGWP = cumsum(NEE) - cumsum(CH4))%>%
  mutate(cumNEECO2 = cumNEESGWP *(44.01/12.01)) %>%
  #mutate(cumNEECO2 = cumsum(NEE) *(44.01/12.01)) %>%
  #mutate(SGWPtotal20 = cumNEECO2 + cumCH4gC20yrSGWP) %>%
  #mutate(SGWPtotal100 = cumNEECO2 + cumCH4gC100yrSGWP)
  mutate(SGWPtotal20 = cumNEECO2 + SGWPcumCH420yr) %>%
  mutate(SGWPtotal100 = cumNEECO2 + SGWPcumCH4100yr)


```

__SGWP__


```{r SGWP}
CO2eq %>%
  dplyr::select(c(Site, SGWPtotal20, month_local)) %>%
  group_by(Site) %>%
  mutate(row = row_number()) %>%
  pivot_wider(names_from = Site, values_from = SGWPtotal20) %>%
  summarise(BB1 = last(na.omit(BB1)),
            BB2 = last(na.omit(BB2))) %>%
  kbl(caption = "20yr SWGP") %>%
  kable_classic(html_font = "Cambria")

CO2eq %>%
  dplyr::select(c(Site, SGWPtotal100, month_local)) %>%
  group_by(Site) %>%
  mutate(row = row_number()) %>%
  pivot_wider(names_from = Site, values_from = SGWPtotal100) %>%
  summarise(BB1 = last(na.omit(BB1)),
            BB2 = last(na.omit(BB2))) %>%
  kbl(caption = "100yr SWGP") %>%
  kable_classic(html_font = "Cambria")
```

### Environmental effects on CO2 fluxes

These transformations have been applied: Fulldata <- Fulldata %>% (NGFflux.input_data)
  mutate(CH4_gC = (ch4gC + 0.03),
         CH4_mgC = (ch4mgC + 26)) %>%
  mutate(logCH4_gC = log(CH4_gC),
         logCH4_mgC = log(CH4_mgC))
         
DONT USE CH4_MGC

GOING TO RECALCULATE MIN TO ADD FOR EACH SITE. 

```{r join flux and environmental data}
setwd(wd)
library(broom)

NGFflux.input_file <- "data/BB_fulldata.csv"
NGFflux.input_data <- read.csv(NGFflux.input_file) %>%
  select(c("Site", "jday", 39:48, )) %>%
  select(-c(logCH4_mgC, logCH4_gC))

NGFflux.input_data$Site <- revalue(NGFflux.input_data$Site, c("BB1"="CA-DBB", "BB2"="CA-DB2")) #rename factors


#To add constant to each site separately (to CH4) for log transformation
NGFflux.input_data %>% filter(Site =="CA-DBB") %>%
  summary()

NGFflux.input_data %>% filter(Site =="CA-DB2") %>%
  summary()

Flux.Env <- right_join(Flux.input_data, Env.input_data,  by = c("jday", "Site")) 
Flux.Env$lnRECO <- log(Flux.Env$RecogC)

ind.GS <- (Flux.Env$jday >= 92 & Flux.Env$jday <= 274)
ind.NGS <- (Flux.Env$jday < 92 | Flux.Env$jday >=275)
Flux.Env$Period <- ''
Flux.Env$Period[ind.GS] <- 'GS'
Flux.Env$Period[ind.NGS] <- 'NGS'

Flux.Env.Ngf <- right_join(Env.input_data, NGFflux.input_data) #Using non gapfilled data
Flux.Env.GF.NGF <- right_join(Flux.Env.Ngf, Flux.Env)

ind.GS <- (Flux.Env.Ngf$jday >= 92 & Flux.Env.Ngf$jday <= 274)
ind.NGS <- (Flux.Env.Ngf$jday < 92 | Flux.Env.Ngf$jday >=275)


Flux.Env.Ngf$Period <- ''
Flux.Env.Ngf$Period[ind.GS] <- 'GS'
Flux.Env.Ngf$Period[ind.NGS] <- 'NGS'

ind.GS <- (Flux.Env.GF.NGF$jday >= 92 & Flux.Env.GF.NGF$jday <= 274)
ind.NGS <- (Flux.Env.GF.NGF$jday < 92 | Flux.Env.GF.NGF$jday >=275)
Flux.Env.GF.NGF$Period <- ''
Flux.Env.GF.NGF$Period[ind.GS] <- 'GS'
Flux.Env.GF.NGF$Period[ind.NGS] <- 'NGS'

Final.output_file <-"data/Final.csv"
write.csv(Flux.Env, Final.output_file)

Final.output_fileNgf <- "data/Nongf.csv"
write.csv(Flux.Env.Ngf, Final.output_fileNgf)

```


__Ecosystem respiration and soil temperature__

For any given soil temperature, respiration is higher at BB2 than BB1.

- Night time gapfilled data

- At BB1, WTH is not a sig important predictor for REco (P= 0.09), however, at BB2, WTH is sig, important in predicting REco (P<0.01). This is because BB2 gets significantly drier, and so dry and warm soil temperatures --> increased respiration rates.

- The relationship look non-linear, so I will use polynomial regression to find which relationship is best for each site.

```{r Reco WTH effect , figures-side, fig.show="hold", out.width="50%"}
#NOTES:
#Compare GS vs. Non GS - could compare the magnitude of difference to see if there is a particular time of year when the influence is higher


(ER.WTH.P <- Flux.Env %>%
  #filter(TS.5_mean > '0') %>%
  ggplot(., aes(WTH._mean, log(RecogC), color= Site)) +
       scale_color_jco()+
   xlab('WTH(cm)')+
   ylab(bquote('Ecosystem respiration (g C' ~m^-2~ day^-1*')'))+
  geom_point()+
   geom_smooth(method = "lm", se = FALSE) + 
    ggtitle("b")+
  theme_bw()+
   theme(legend.position = "none", axis.text = element_text(size = 14),
          axis.title = element_text(size = 15),
         axis.text.y = element_blank(),
         axis.title.y = element_blank()))

(ER.WTH.GS.P <- Flux.Env %>%
  filter(Period == 'GS') %>%
  ggplot(., aes(WTH._mean, RecogC, color= Site)) +
       scale_color_jco()+
   xlab('WTH(cm)')+
   ylab(bquote('Ecosystem respiration (g C' ~m^-2~ day^-1*')'))+
  geom_point()+
    geom_smooth(method = "lm", se = FALSE)+
  theme_bw()+
        ggtitle("Growing season")+
    theme(legend.position = "none",
          axis.text = element_text(size = 12),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_blank()))

(ER.WTH.NGS.P <- Flux.Env %>%
  filter(Period == 'NGS') %>%
  ggplot(., aes(WTH._mean, RecogC, color= Site)) +
       scale_color_aaas()+
   xlab('WTH(cm)')+
   ylab(bquote('Ecosystem respiration (g C' ~m^-2~ day^-1*')'))+
  geom_point()+
        geom_smooth(method = "lm", se = FALSE)+
    ggtitle("Non-growing season")+
  theme_bw()+
  theme(axis.text = element_text(size = 12),
          axis.title.x = element_text(size = 12),
        axis.title.y = element_blank()))

ggarrange(ER.WTH.P, ER.WTH.GS.P, ER.WTH.NGS.P, nrow = 1, ncol = 3, common.legend = TRUE, widths = c(1, .9, .9))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/RecoWTH.tiff", width = 8, height = 4, device='tiff', dpi=300)


RECO_WTH <- aov(RecogC~WTH._mean*Site, Flux.Env)
summary(RECO_WTH)
```


```{r split BB1 and BB2 data 1st time}
BB1 <- Flux.Env %>%
  filter(Site == "CA-DBB") %>%
  mutate(lnRECO = log(RecogC))
#%>%
  #drop_na(WTH._mean)

BB2 <- Flux.Env %>%
  filter(Site == "CA-DB2") %>%
    mutate(lnRECO = log(RecogC))

```
 

__BB1__ 

Calculate Q10 for ecosystem respiration. Tutorial from https://stackoverflow.com/questions/66060024/how-to-get-the-paremeters-when-i-have-a-given-data-and-formula-in-r 

```{r BB1 Reco Q10}
#Annual
#nlsfitBB1.annual <- nls(RecogC ~ a*exp(b*BB1$TS.5_mean), data = BB1, start = list(a = 0.1, b = 0.1))

#coefs.BB1annual <- coef(nlsfitBB1.annual)
#coefs.BB1annual

#plot(BB1$TS.5_mean, BB1$RecogC)
#lines(BB1$TS.5_mean, coefs.BB1annual[["a"]]*exp(coefs.BB1annual[["b"]]*BB1$TS.5_mean))

#Q10.BB1annual <- exp(10*coefs.BB1annual[["b"]])
#Q10.BB1annual

#a.annBB1 <- 0.1272996
#b.annBB1 <- 0.1399094 

#### OR IF USING LOG:
shapiro.test(BB1$lnRECO)

Q10.RECO.BB1 <- lm(lnRECO~TS.5_mean, data = BB1)
summary(Q10.RECO.BB1)
#ln(RECO) = -2 + 0.12(TS)
lnQ10.BB1 <- exp(10*0.12)


Q10.RECO.BB2 <- lm(lnRECO~TS.5_mean, data = BB2)
summary(Q10.RECO.BB2)
#ln(RECO) = -0.9 + 0.09(TS)
lnQ10.BB2 <- exp(10*0.09)

#GS
BB1.GS <- BB1 %>% filter(Period.y =="GS")
nlsfit.GS.CO2BB1 <- nls(RecogC ~ a*exp(b*BB1.GS$TS.5_mean), data = BB1.GS, start = list(a = 0.1, b = 0.1))

coefs.GS.CO2BB1 <- coef(nlsfit.GS.CO2BB1)
coefs.GS.CO2BB1

plot(BB1.GS$TS.5_mean, BB1.GS$RecogC)
lines(BB1.GS$TS.5_mean, coefs.GS.CO2BB1[["a"]]*exp(coefs.GS.CO2BB1[["b"]]*BB1.GS$TS.5_mean))

Q10.GS.GS.CO2BB1 <- exp(10*coefs.GS.CO2BB1[["b"]])
Q10.GS.GS.CO2BB1

a.GSBB1CO2 <- 0.04979863
b.GSBB1CO2 <- 0.19540514

TS.BB1.modGS <- lm(RecogC~TS.5_mean, data = BB1.GS)
MASS::boxcox(TS.BB1.modGS)
summary(TS.BB1.modGS)

#NGS
BB1.NGS <- BB1 %>% filter(Period.y =="NGS")
nlsfit.NGS.CO2BB1 <- nls(RecogC ~ a*exp(b*BB1.NGS$TS.5_mean), data = BB1.NGS, start = list(a = 0.1, b = 0.1))

coefs.NGS.CO2BB1 <- coef(nlsfit.NGS.CO2BB1)
coefs.NGS.CO2BB1

plot(BB1.NGS$TS.5_mean, BB1.NGS$RecogC)
lines(BB1.NGS$TS.5_mean, coefs.NGS.CO2BB1[["a"]]*exp(coefs.NGS.CO2BB1[["b"]]*BB1.NGS$TS.5_mean))

Q10.NGS.CO2BB1 <- exp(10*coefs.NGS.CO2BB1[["b"]])
Q10.NGS.CO2BB1

a.NGSBB1CO2 <- 0.21284189
b.NGSBB1CO2 <- 0.09413844

TS.BB1.modNGS <- lm(RecogC~TS.5_mean, data = BB1.NGS)
MASS::boxcox(TS.BB1.modNGS)
summary(TS.BB1.modNGS)

test <- ggplot(BB1.NGS, aes(jday, RecogC))+geom_point()
ggplotly(test)

TS.BB1.mod <- lm(RecogC~TS.5_mean, data = BB1)
MASS::boxcox(TS.BB1.mod)
summary(TS.BB1.mod)

TS.BB2.mod <- lm(RecogC~TS.5_mean, data = BB2)
MASS::boxcox(TS.BB2.mod)
summary(TS.BB2.mod)

TS5.ER <- aov(RecogC~TS.5_mean*Site, data = Flux.Env)
summary(TS5.ER)
```


```{r BB2 Reco Q10}
# Annual
nlsfitBB2.annual <- nls(RecogC ~ a*exp(b*BB2$TS.5_mean), data = BB2, start = list(a = 0.1, b = 0.1))

coefs.BB2annual <- coef(nlsfitBB2.annual)
coefs.BB2annual

plot(BB2$TS.5_mean, BB2$RecogC)
lines(BB2$TS.5_mean, coefs.BB2annual[["a"]]*exp(coefs.BB2annual[["b"]]*BB2$TS.5_mean))

Q10.BB2annual <- exp(10*coefs.BB2annual[["b"]])
Q10.BB2annual

a.annBB2 <- 0.45054453
b.annBB2 <- 0.08833384


#GS
BB2.GS <- BB2 %>% filter(Period =="GS")
nlsfit.GS.CO2BB2 <- nls(RecogC ~ a*exp(b*BB2.GS$TS.5_mean), data = BB2.GS, start = list(a = 0.1, b = 0.1))

coefs.GS.CO2BB2 <- coef(nlsfit.GS.CO2BB2)
coefs.GS.CO2BB2

plot(BB2.GS$TS.5_mean, BB2.GS$RecogC)
lines(BB2.GS$TS.5_mean, coefs.GS.CO2BB2[["a"]]*exp(coefs.GS.CO2BB2[["b"]]*BB2.GS$TS.5_mean))

Q10.GS.GS.CO2BB2 <- exp(10*coefs.GS.CO2BB2[["b"]])
Q10.GS.GS.CO2BB2

a.GSBB2CO2 <- 0.42124984
b.GSBB2CO2 <- 0.09207058

TS.BB2.modGS <- lm(RecogC~TS.5_mean, data = BB2.GS)
MASS::boxcox(TS.BB2.modGS)
summary(TS.BB2.modGS)

#NGS
BB2.NGS <- BB2 %>% filter(Period =="NGS")
nlsfit.NGS.CO2BB2 <- nls(RecogC ~ a*exp(b*BB2.NGS$TS.5_mean), data = BB2.NGS, start = list(a = 0.1, b = 0.1))

coefs.NGS.CO2BB2 <- coef(nlsfit.NGS.CO2BB2)
coefs.NGS.CO2BB2

plot(BB2.NGS$TS.5_mean, BB2.NGS$RecogC)
lines(BB2.NGS$TS.5_mean, coefs.NGS.CO2BB2[["a"]]*exp(coefs.NGS.CO2BB2[["b"]]*BB2.NGS$TS.5_mean))

Q10.NGS.CO2BB2 <- exp(10*coefs.NGS.CO2BB2[["b"]])
Q10.NGS.CO2BB2

a.NGSBB2CO2 <- 0.43806467
b.NGSBB2CO2 <- 0.09516392

TS.BB2.modNGS <- lm(RecogC~TS.5_mean, data = BB2.NGS)
MASS::boxcox(TS.BB2.modNGS)
summary(TS.BB2.modNGS)
```

```{r Reco Temp}
library(ggpubr)

TS.BB1.mod <- lm(RecogC~TS.5_mean, data = BB1)
MASS::boxcox(TS.BB1.mod)
plot(TS.BB1.mod)
summary(TS.BB1.mod)


(ER.TS5.P <- Flux.Env %>%
  #filter(TS.5_mean > '0') %>%
  ggplot(., aes(TS.5_mean, RecogC, color= Site)) +
       scale_color_jco()+
   xlab('5cm Soil temperature (°C)')+
   ylab(bquote('RECO (g C' ~m^-2~ day^-1*')'))+
  geom_point()+
  stat_function(fun=function(x) a.annBB1*exp(b.annBB1*x), colour = "red")+
  stat_function(fun=function(x) a.annBB2*exp(b.annBB2*x), colour = "darkblue")+
    ggtitle("a")+
  theme_bw()+
   theme(legend.position = "none",
          axis.text = element_text(size = 12),
          axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12)))

ER.TS5GS.P <- Flux.Env %>%
  filter(Period == "GS") %>%
  ggplot(., aes(TS.5_mean, RecogC, color= Site)) +
       scale_color_aaas()+
   xlab('5cm Soil temperature (°C)')+
   ylab(bquote('RECO (g C' ~m^-2~ day^-1*')'))+
  geom_point()+
  stat_function(fun=function(x) a.GSBB1CO2*exp(b.GSBB1CO2*x), colour = "")+
  stat_function(fun=function(x) a.GSBB2CO2*exp(b.GSBB2CO2*x), colour = "darkblue")+
ggtitle("b.) Growing season")+
  theme_bw()+
    theme(legend.position = "none",
          axis.title.y = element_blank(),
          axis.text = element_text(size = 12),
          axis.title.x = element_text(size = 12))

ER.TS5NGS.P <- Flux.Env %>%
  filter(Period == "NGS") %>%
  ggplot(., aes(TS.5_mean, RecogC, color= Site)) +
       scale_color_aaas()+
   xlab('5cm Soil temperature (°C)')+
   ylab(bquote('RECO (g C' ~m^-2~ day^-1*')'))+
  geom_point()+
  stat_function(fun=function(x) a.NGSBB1CO2*exp(b.NGSBB1CO2*x), colour = "red")+
  stat_function(fun=function(x) a.NGSBB2CO2*exp(b.NGSBB2CO2*x), colour = "darkblue")+
ggtitle("c.) Non-growing season")+
  theme_bw()+
    theme(axis.title.y = element_blank(),
          axis.text = element_text(size = 12),
          axis.title.x = element_text(size = 12),
          legend.title = element_text(size = 15),
          legend.text = element_text(size = 14))

ggarrange(ER.TS5.P, ER.TS5GS.P, ER.TS5NGS.P, nrow = 1, ncol = 3, common.legend = TRUE, widths = c(1, 0.9, 0.9))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/RecoTemp.tiff", width = 8, height = 4, device='tiff', dpi=300)

```




For BB1, 2 models to predict Reco were very similar (model 4(with WTH) and model 7). Thinking of going with model 7, which doesn't include WTH. Within sites, how important is WTH in explaining Reco? Need to check model assumptions. Including water table height does not sig improve (0.09) model. Therefore Reco at BB1 is predominately driven by temperature, and not WTH.

```{r BB1 model reln between Reco and Temp and WTH}
# Polynomial regression: Check for non-linear relationships #http://www.sthda.com/english/articles/40-regression-analysis/162-nonlinear-regression-essentials-in-r-polynomial-and-spline-regression-models/
cor.test(BB1$WTH._mean, BB1$TS.5_mean)

# Build the models
#model.3 <- lm(RecogC~ TS.5_mean, data = BB1)
model.4 <- lm(RecogC~ TS.5_mean + I(TS.5_mean^3) + WTH._mean, data = BB1) # Model with highest R2, only slightly higher than model without WTH (model 7)., but WTH isn't actually a significant predictor so will use model 7
model.5 <- lm(RecogC ~ log(TS.5_mean), data = BB1)
model.7 <- lm(RecogC~ TS.5_mean + I(TS.5_mean^3), data = BB1)  # use this model 
model.8 <- lm(log(RecogC)~ WTH._mean, data = BB1)
model.9 <- lm(log(RecogC)~ TS.5_mean * WTH._mean, data = BB1)
model.10 <- lm(log(RecogC)~ TS.5_mean, data = BB1)
model.11 <- lm(log(RecogC)~ TS.5_mean + WTH._mean, data = BB1)


model.sel(model.8, model.9, model.11)

summary(model.11)
summary(model.3)
#summ(model.4)
#summ(model.7)  # need to check if ols is meeting assumptions
```
DONT NEED GPP MODELS
```{r models for GPP BB1}
# Build the models
model.3 <- lm(GPPgC_f~ TS.5_mean, data = BB1)
model.8 <- lm(GPPgC_f~ WTH._mean, data = BB1)
model.9 <- lm(GPPgC_f~ TS.5_mean * WTH._mean, data = BB1)

summary(model.8)
model.sel(model.3, model.8, model.9)

cor.test(Flux.Env$TS.5_mean, Flux.Env$WTH._mean)
```
```{r models for GPP BB2}
cor.test(BB2$TS.5_mean, BB2$WTH._mean)

# Build the models
model.3 <- lm(GPPgC_f~ TS.5_mean, data = BB2)
model.8 <- lm(GPPgC_f~ WTH._mean, data = BB2)
model.9 <- lm(GPPgC_f~ TS.5_mean * WTH._mean, data = BB2)

summary(model.8)
model.sel(model.3, model.8, model.9)

GPP.TS.5 <- aov(GPPgC_f~WTH._mean*Site, data = Flux.Env)
summary(GPP.TS.5)
```

__BB2__ 

At BB2, including WTH in the model sig. (P<0.05) improves it. BB2 gets significantly drier than BB1, which is why there is such a strong control of WTH on Reco? 

```{r BB2 model reln between Reco and Temp and WTH, figures-side, fig.show="hold", out.width="50%"}
# Polynomial regression: Check for non-linear relationships http://www.sthda.com/english/articles/40-regression-analysis/162-nonlinear-regression-essentials-in-r-polynomial-and-spline-regression-models/

# Build the models
model.1 <- lm(RecogC~ poly(TS.5_mean, 3, raw = TRUE), data = BB2)
model.2 <- lm(RecogC~ poly(TS.5_mean, 2, raw = TRUE), data = BB2)
model.3 <- lm(log(RecogC)~ TS.5_mean, data = BB2)
model.4 <- lm(RecogC~ TS.5_mean + I(TS.5_mean^3)+ WTH._mean, data = BB2) #need to check distribution.. i.e. is it normal? highest R2
model.5 <- lm(RecogC ~ log(TS.5_mean), data = BB2)
model.6 <- lm(log(RecogC) ~ TS.5_mean, data = BB2)
model.7 <- lm(RecogC ~ TS.5_mean + I(TS.5_mean^3), data = BB2) #model with 2nd highest R2
model.wth.BB2 <- lm(log(RecogC)~ WTH._mean, data = BB2)
model.8.BB2 <- lm(log(RecogC)~ TS.5_mean + WTH._mean, data = BB2)

cor.test(BB2$TS.5_mean, BB2$WTH._mean, method = "pearson")

#summ(model.7) # need to check if ols is meeting assumptions
#summ(model.4)

summary(model.wth.BB2)
#summary(model.4)

model.sel(model.3, model.wth.BB2, model.8.BB2)
```


When comparing the two sites, note that whilst WTH was not a sig. important predictor for BB1, I have included it in the figure.
In both figures the plotted line does not take into account WTH, but is y ~ x + x^3

```{r compare BB1 and BB2 Reco, figures-side, fig.show="hold", out.width="50%"}
(modelCO2.bb1.p<- BB1 %>% 
   drop_na(WTH._mean) %>%
   ggplot(., aes(TS.5_mean, RecogC)) +
  geom_point(aes(color = WTH._mean), na.rm = TRUE) +
   stat_function(fun=function(x) a.annBB1*exp(b.annBB1*x))+
  scale_color_gradient(low = "light blue", high = "dark blue", limits = c(-40,20))+
  scale_y_continuous(limits = c(0,3.5))+
     scale_x_continuous(limits = c(0,20))+
  xlab("5cm soil temperature (°C)")+
  ylab(bquote('RECO (g C' ~m^-2~ day^-1*')'))+
   labs(color = "WTH") +
  ggtitle("a")+
  theme_bw() +
   theme(axis.text = element_text(size = 12),
          axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12) ))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/RecoTempWTH.tiff", width = 4, height = 4, device='tiff', dpi=300)


(modelCO2.bb2.p <- ggplot(BB2, aes(TS.5_mean, RecogC)) +
  geom_point(aes(color = WTH._mean)) +
      stat_function(fun=function(x) a.annBB2*exp(b.annBB2*x)) +
  scale_color_gradient(low = "light blue", high = "dark blue", limits = c(-40,20))+
  scale_y_continuous(limits = c(0,3.5))+
  #stat_smooth(method = lm, formula = y ~ x + I(x^3))+
  xlab("5cm soil temperature (°C)")+
  ylab(bquote('RECO (g C' ~m^-2~ day^-1*')'))+
    labs(color= "WTH")+
  ggtitle("b")+
  theme_bw()+
  theme()+
   theme(axis.text = element_text(size = 12),
          axis.title.x = element_text(size = 12),
         axis.title.y = element_blank(),
         axis.text.y = element_blank()))


ggarrange(modelCO2.bb1.p, modelCO2.bb2.p, nrow = 1, ncol = 2, common.legend = TRUE, widths = c(1.1, 1))
ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/RecoTempWTH.tiff", width = 6, height = 4, device='tiff', dpi=300)


#LOGGED RECO

(modelCO2.bb1.p<- BB1 %>% 
   drop_na(WTH._mean) %>%
   ggplot(., aes(TS.5_mean, lnRECO)) +
  geom_point(aes(color = WTH._mean), na.rm = TRUE) +
    stat_smooth(method = "lm", se = FALSE, color = "black", size = 0.5)+
   #stat_function(fun=function(x) BB1.int+(BB1.coef*x))+
  scale_color_gradient(low = "light blue", high = "dark blue", limits = c(-40,20))+
  scale_y_continuous(limits = c(-3,1.5))+
     scale_x_continuous(limits = c(0,20))+
  xlab("5cm soil temperature (°C)")+
  ylab(bquote('lnRECO (g C' ~m^-2~ day^-1*')'))+
   labs(color = "WTH") +
  ggtitle("b")+
  theme_bw() +
   theme( axis.text = element_text(size = 12),
          axis.title.x = element_text(size = 12),
         axis.title.y = element_blank(),
         axis.text.y = element_blank()))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/RecoTempWTH.tiff", width = 4, height = 4, device='tiff', dpi=300)


(modelCO2.bb2.p <- ggplot(BB2, aes(TS.5_mean, lnRECO)) +
  geom_point(aes(color = WTH._mean))+
      #stat_function(fun=function(x) BB2.int+(BB2.coef*x)) +
  scale_color_gradient(low = "light blue", high = "dark blue", limits = c(-40,20))+
  scale_y_continuous(limits = c(-3,1.5))+
  stat_smooth(method = lm, se = FALSE, color = "black", size = 0.5)+
  xlab("5cm soil temperature (°C)")+
  ylab(bquote('lnRECO (g C' ~m^-2~ day^-1*')'))+
    labs(color= "WTH")+
  ggtitle("a")+
  theme_bw()+
  theme()+
   theme(axis.text = element_text(size = 12),
          axis.title.x = element_text(size = 12),
         axis.title.y = element_text(size = 12)))


ggarrange(modelCO2.bb2.p, modelCO2.bb1.p, nrow = 1, ncol = 2, common.legend = TRUE, widths = c(1.1, 1))
ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/RecoTempWTHln.tiff", width = 6, height = 4, device='tiff', dpi=300)

```


__GPP and PAR__

```{r GPP and PAR, warning = FALSE}
GPP.BB1 <- read.csv('/Users/marionnyberg/Google\ Drive/Micromet\ Lab/Projects/2014-Burns\ Bog/Flux-tower/flux_data/BB_L3.csv') %>% filter(DATE >= '2020-01-01 00:00'& DATE <= '2021-01-01 00:00') %>% select(GPP_f, jday, co2_flux, DATE)
GPP.BB1$Site <- "CA-DBB"
GPP.BB1$DATE <- as.POSIXct(GPP.BB1$DATE, format = "%Y-%m-%dT%H:%M:%SZ", tz="UTC")
GPP.BB1 <- full_join(GPP.BB1, Parin) # join par and co2 data

GPP.BB2 <- read.csv('/Users/marionnyberg/Google\ Drive/Micromet\ Lab/Projects/2019-Burns\ Bog\ 2/Flux-tower/flux_data/BB2_L3.csv')%>% filter(DATE >= '2020-01-01 00:00' & DATE <= '2021-01-01 00:00') %>% select(GPP_f, jday, co2_flux, DATE)
GPP.BB2$Site <- "CA-DB2"
GPP.BB2$DATE <- as.POSIXct(GPP.BB2$DATE, format = "%Y-%m-%d %H:%M:%S", tz="UTC")

GPP.BB2 <- full_join(GPP.BB2, Parin)

GPP <- full_join(GPP.BB1, GPP.BB2) %>% filter(INCOMING_PAR > '0.01')
```

```{r NEE and PAR}
(NEEPAR.p <-GPP %>% #filter(co2gC<5) %>%
  ggplot(., aes(INCOMING_PAR, co2_flux, color = Site)) +
  geom_point()+
   #geom_smooth(method = "lm", aes(colour = Site)) +
      #stat_function(fun=function(x) B*(GPPPAR.1$co2gC) + R, colour = "red")+
  #scale_colour_manual(values = c("#0072B2", "#D55E00")) +
  ylab(bquote('NEE (g C' ~m^-2~ day^-1*')'))+
    xlab('PAR')+
    scale_color_jco()+
  theme_bw())

NEEPAR <- aov(co2_flux~INCOMING_PAR*Site, data = GPP)
summary(NEEPAR)

#BB1 GS
GPP.BB1.gs <- GPP.BB1 %>% filter(Period =="GS" & GPP_f > 0 & GPP_f <20) 
#GPP.BB1.gs <- GPP.BB1.gs %>% mutate(NEE.GPP = co2_flux * -1) %>% filter(NEE.GPP > -20 & NEE.GPP < 20)

#model <- nls(NEE.GPP ~ (a*GPP.BB1.gs$INCOMING_PAR)*b/(a*GPP.BB1.gs$INCOMING_PAR+b), start=list(a = 0.1, b = 0.1), data = GPP.BB1.gs)

#coefs.Modelbb1 <- coef(model)
#coefs.Modelbb1
#a <- 0.005
#b <- 4.26

#plot(GPP.BB1.gs$INCOMING_PAR, GPP.BB1.gs$NEE.GPP)
#lines(GPP.BB1.gs$INCOMING_PAR,predict(model), col = "red")

#nls fit SIMILAR TO NINGYU'S PAPER
#ggplot(GPP.BB1.gs, aes(INCOMING_PAR, NEE.GPP)) + geom_point() + 
 # stat_function(fun=function(x) (a*x)*b/(a*x+b), colour = "red") +
  #theme_bw()

#using GPP - results look better?
model.GPP <- nls(GPP_f ~ (a*GPP.BB1.gs$INCOMING_PAR)*b/(a*GPP.BB1.gs$INCOMING_PAR+b), start=list(a = 0.1, b = 0.1), data = GPP.BB1.gs)

summary(model.GPP)

coefs.Modelbb1.GPP <- coef(model.GPP)
coefs.Modelbb1.GPP
a.GPP <- 0.017
b.GPP <- 4.58

ggplot(GPP.BB1.gs, aes(INCOMING_PAR, GPP_f)) + geom_point() + 
  stat_function(fun=function(x) (a.GPP*x)*b.GPP/(a.GPP*x+b.GPP), colour = "red") +
      ylab(bquote('Incoming PAR (umol'  ~m^-2~day^-1*')'))+
  theme_bw()

#BB2 GS
GPP.BB2.gs <- GPP.BB2 %>% filter(Period =="GS" & GPP_f > 0 & GPP_f < 20) 
#GPP.BB2.gs <- GPP.BB2.gs %>% mutate(NEE.GPP = co2_flux * -1) %>% filter(NEE.GPP > -20 & NEE.GPP < 20)

#model.2 <- nls(NEE.GPP ~ (a*GPP.BB2.gs$INCOMING_PAR)*b/(a*GPP.BB2.gs$INCOMING_PAR+b), start=list(a = 0.1, b = 0.1), data = GPP.BB2.gs)

#coefs.Modelbb2 <- coef(model.2)
#coefs.Modelbb2
#a <- 0.006
#b <- 4.25

#plot(GPP.BB2.gs$INCOMING_PAR, GPP.BB2.gs$NEE.GPP)
#lines(GPP.BB2.gs$INCOMING_PAR,predict(model.2), col = "red")

#using GPP - results look better?
model.GPP.2 <- nls(GPP_f ~ (a*GPP.BB2.gs$INCOMING_PAR)*b/(a*GPP.BB2.gs$INCOMING_PAR+b), start=list(a = 0.1, b = 0.1), data = GPP.BB2.gs)

summary(model.GPP.2)

coefs.Modelbb2.GPP <- coef(model.GPP.2)
coefs.Modelbb2.GPP
a.GPP.2 <- 0.025
b.GPP.2 <- 5.5

ggplot(GPP.BB2.gs, aes(INCOMING_PAR, GPP_f)) + geom_point() + 
  stat_function(fun=function(x) (a.GPP.2*x)*b.GPP.2/(a.GPP.2*x+b.GPP.2), colour = "red") +
      ylab(bquote('Incoming PAR (umol'  ~m^-2~day^-1*')'))+
  theme_bw()

LUE <- aov(GPP_f~INCOMING_PAR*Site, data = GPP)
summary (LUE)
```

```{r LIGHT RESPONSE CURVE GS}
#Both sites together (GS):
(GS.LR <- GPP %>% filter(Period == "GS" & INCOMING_PAR > 10 & GPP_f > 0 & GPP_f < 20) %>%
  ggplot(., aes(INCOMING_PAR, GPP_f), group = Site) + geom_point(aes(color = Site))+
  scale_color_jco()+
    stat_function(fun=function(x) (a.GPP*x)*b.GPP/(a.GPP*x+b.GPP), colour = "#EFC000FF") +
  stat_function(fun=function(x) (a.GPP.2*x)*b.GPP.2/(a.GPP.2*x+b.GPP.2), colour = "#0073C2FF") +
        xlab(bquote('Incoming PAR ('*mu~'mol' ~m^-2~s^-1*')'))+
          ylab(bquote('GPP ('*mu~'mol'  ~m^-2~s^-1*')'))+
  ggtitle("a")+
  theme(axis.text = element_text(size = 14),
          axis.title.x = element_text(size = 15),
         axis.title.y = element_text(size = 15))+
  theme_bw())


ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/LUE.tiff", width = 6, height = 4, device='tiff', dpi=300)
```

```{r LIGHT RESPONSE CURVE NGS}
#BB1 NGS
GPP.BB1.ngs <- GPP.BB1 %>% filter(Period =="NGS" & GPP_f > 0 & GPP_f < 20) 
#GPP.BB1.ngs <- GPP.BB1.ngs %>% mutate(NEE.opp = co2_flux * -1) #%>% filter(NEE.GPP > -20 & NEE.GPP < 20)


#using GPP - results look better?
model.GPP.ngs <- nls(GPP_f ~ (a*GPP.BB1.ngs$INCOMING_PAR)*b/(a*GPP.BB1.ngs$INCOMING_PAR+b), start=list(a = 0.1, b = 0.1), data = GPP.BB1.ngs)

summary(model.GPP.ngs)

coefs.Modelbb1.GPP.ngs <- coef(model.GPP.ngs)
coefs.Modelbb1.GPP.ngs
a.GPP.ngs <- 0.01
b.GPP.ngs <- 1.5

ggplot(GPP.BB1.ngs, aes(INCOMING_PAR, GPP_f)) + geom_point() + 
  stat_function(fun=function(x) (a.GPP.ngs*x)*b.GPP.ngs/(a.GPP.ngs*x+b.GPP.ngs), colour = "red") +
      xlab(bquote('Incoming PAR (umol'  ~m^-2~day^-1*')'))+
  scale_y_continuous(limits = c(-10, 10))+
  theme_bw()

#BB2 NGS
GPP.BB2.ngs <- GPP.BB2 %>% filter(Period =="NGS" & GPP_f >0 & GPP_f < 20) 
#GPP.BB2.ngs <- GPP.BB2.ngs %>% mutate(NEE.GPP = co2_flux * -1) %>% filter(NEE.GPP > '-20' & NEE.GPP < '20')

#using GPP - results look better?
model.GPP.2ngs <- nls(GPP_f ~ (a*GPP.BB2.ngs$INCOMING_PAR)*b/(a*GPP.BB2.ngs$INCOMING_PAR+b), start=list(a = 0.1, b = 0.1), data = GPP.BB2.ngs)
summary(model.GPP.2ngs)

coefs.Modelbb2.GPPngs <- coef(model.GPP.2ngs)
coefs.Modelbb2.GPPngs
a.GPP.2ngs <- 0.015
b.GPP.2ngs <- 2.57

ggplot(GPP.BB2.ngs, aes(INCOMING_PAR, GPP_f)) + geom_point() + 
  stat_function(fun=function(x) (a.GPP.2ngs*x)*b.GPP.2ngs/(a.GPP.2ngs*x+b.GPP.2ngs), colour = "red") +
      ylab(bquote('Incoming PAR (umol'  ~m^-2~day^-1*')'))+
  theme_bw()

#Both sites together (NGS):
(NGS.lr <- GPP %>% filter(Period == "NGS" & INCOMING_PAR > 10 & GPP_f > 0 & GPP_f < 20) %>%
  ggplot(., aes(INCOMING_PAR, GPP_f), group = Site) + geom_point(aes(color = Site))+
  scale_color_jco()+
    stat_function(fun=function(x) (a.GPP.ngs*x)*b.GPP.ngs/(a.GPP.ngs*x+b.GPP.ngs), colour = "#EFC000FF") +
  stat_function(fun=function(x) (a.GPP.2ngs*x)*b.GPP.2ngs/(a.GPP.2ngs*x+b.GPP.2ngs), colour = "#0073C2FF") +
        xlab(bquote('Incoming PAR ('*mu~'mol' ~m^-2~s^-1*')'))+
          ylab(bquote('GPP ('*mu~'mol' ~m^-2~s^-1*')'))+
  ggtitle("b") +
  theme(axis.title.y = element_blank(),
        axis.text = element_text(size = 14),
          axis.title.x = element_text(size = 15))+
         #axis.title.y = element_text(size = 12))+
  theme_bw())

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/LUEngs.tiff", width = 6, height = 4, device='tiff', dpi=300)



(lightresposne.arranged <- ggarrange(GS.LR, NGS.lr, ncol = 2, common.legend = TRUE, align = "h", widths=c(1, 1)))


ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/LRarranged.tiff", width = 6, height = 4, device='tiff', dpi=330)

```

### Environmental effects on CH4 fluxes


__CH4 and temperature response__

Non-linear response to temperature. CH4 has a constant added and is log transformed. Response looks fairly similar between sites...


__WTH and CH4__

- WTD : follow instructions from Turetsky in regards to filtering out values so that we are comparing the same things. This will just make is easier to assess the difference in temperature response between the 2 sites, and does not reflect the different in WTD between the sites.

The relationship look non-linear. I will use a similar data analysis technique as shown in fig. 5 of the Turetsky paper: 'Correlation of temperature sensitivity and CH4 flux and the optimal water table position.'

It would be good to plot a timeseries of WTH and CH4 flux as in Brown et al (2014). Also fig. 5 could be a way to plot CH4/WTH/Soil temp relations


```{r CH4 Temp response}
library(car)

```

```{r split BB1 and BB2 data}
#Flux.Env.Ngf$logCH4_mgC <- log(Flux.Env.Ngf$ch4mgC.C)

BB1 <- Flux.Env.GF.NGF %>%
  filter(Site == "CA-DBB") %>%
  mutate(ch4mgC.C = ch4mgC + 8) %>%
  mutate(logCH4_mgC = log(ch4mgC.C)) %>%
  filter(logCH4_mgC > 0)

BB2 <- Flux.Env.GF.NGF %>%
  filter(Site == "CA-DB2") %>%
  filter(ch4mgC > -20) %>%
  mutate(ch4mgC.C = ch4mgC + 20) %>%
  mutate(logCH4_mgC = log(ch4mgC.C))

Flux.Env.Ngf <- full_join(BB1, BB2)

shapiro.test(Flux.Env.Ngf$logCH4_mgC)
```

```{r CH4 Q10 BB1}
# AnnualUSE THE EXPONENTIAL FIT THAT IS CH4_MCG (NOT LNCH4_MGC)
#nlsfit.annualBB1.CH4 <- nls(logCH4_mgC ~ a*exp(b*BB1$TS.5_mean), data = BB1, start = list(a = 0.1, b = 0.1))
#summary(nlsfit.annualBB1.CH4)

nlsfit.annualBB1.CH4 <- nls(CH4_mgC ~ a*exp(b*BB1$TS.5_mean), data = BB1, start = list(a = 0.1, b = 0.1))
summary(nlsfit.annualBB1.CH4)
Q10.annualBB1.CH4 <- exp(10*coefs.annualBB1.CH4[["b"]])

linear.temp.bb1 <- lm (logCH4_mgC~TS.5_mean, data = BB1)
summary(linear.temp.bb1)
lnQ10.BB1 <- exp(10*0.15)


#coefs.annualBB1.CH4 <- coef(nlsfit.annualBB1.CH4)
#coefs.annualBB1.CH4

#plot(BB1$TS.5_mean, BB1$logCH4_mgC)
#lines(BB1$TS.5_mean, coefs.annualBB1.CH4[["a"]]*exp(coefs.annualBB1.CH4[["b"]]*BB1$TS.5_mean))

#Q10.annualBB1.CH4 <- exp(10*coefs.annualBB1.CH4[["b"]])
#Q10.annualBB1.CH4

#a.BB1 <- 2.00939773
#b.BB1 <- 0.04540436
```

```{r CH4 Q10 BB2}
# Annual - USE THE EXPONENTIAL FIT THAT IS CH4_MCG (NOT LNCH4_MGC)
#nlsfit.AnnualBB2.CH4 <- nls(logCH4_mgC ~ a*exp(b*BB2$TS.5_mean), data = BB2, start = list(a = 0.1, b = 0.1))
#summary(nlsfit.AnnualBB2.CH4)

nlsfit.AnnualBB2.CH4 <- nls(CH4_mgC ~ a*exp(b*BB2$TS.5_mean), data = BB2, start = list(a = 0.1, b = 0.1))
summary(nlsfit.AnnualBB2.CH4)
#(Q10.AnnualBB2.CH4 <- exp(10*coefs.AnnualBB2.CH4[["b"]]))

linear.temp.bb2 <- lm (logCH4_mgC~TS.5_mean, data = BB2)
summary(linear.temp.bb2)
lnQ10.BB2 <- exp(10*0.07)


#coefs.AnnualBB2.CH4 <- coef(nlsfit.AnnualBB2.CH4)
#coefs.AnnualBB2.CH4

#plot(BB2$TS.5_mean, BB2$logCH4_mgC)
#lines(BB2$TS.5_mean, coefs.AnnualBB2.CH4[["a"]]*exp(coefs.AnnualBB2.CH4[["b"]]*BB2$TS.5_mean))

#(Q10.AnnualBB2.CH4 <- exp(10*coefs.AnnualBB2.CH4[["b"]]))

#a.BB2 <- 3.00508092
#b.BB2 <- 0.01801396 
```

```{r CH4 temp response, figures-side, fig.show="hold", out.width="50%"}
#(Temp.logCH4<- Flux.Env.Ngf %>%  
 #        #filter(logCH4_mgC > 2) %>%
  #ggplot(., aes(TS.5_mean,logCH4_mgC, color= Site)) +
   #       scale_color_aaas()+
    # ylab(bquote('log F'~CH[4]~ '(mg C' ~m^-2~ day^-1*')'))+
   #xlab('5cm soil temperature (°C)')+
  #geom_point() +
  #stat_function(fun=function(x) a.BB1*exp(b.BB1*x), colour = "red")+
  #stat_function(fun=function(x) a.BB2*exp(b.BB2*x), colour = "darkblue")+
  #  ggtitle("a.) Annual")+
  #theme_bw()+
  # theme(legend.position = "none",
   #      axis.text = element_text(size = 12),
    #      axis.title.x = element_text(size = 12),
     #     axis.title.y = element_text(size = 12)))

TS.BB1.modGS <-lm(logCH4_mgC~TS.5_mean, data = BB1.GS)
MASS::boxcox(TS.BB1.modGS)
summary(TS.BB1.modGS)
RMSE.TS.BB1 <- sqrt(mean(residuals(TS.BB1.modGS)^2))

TS.BB2.modGS <-lm(logCH4_mgC~TS.5_mean, data = BB2.GS)
MASS::boxcox(TS.BB2.modGS)
summary(TS.BB2.modGS)
RMSE.TS.BB2 <- sqrt(mean(residuals(TS.BB2.mod)^2))

Temp.logCH4GS<- Flux.Env.Ngf %>% #don't need to log transform CH4? 
         filter(#logCH4_mgC > 2,
                Period == "GS") %>%
  ggplot(., aes(TS.5_mean,logCH4_mgC, color= Site)) +
          scale_color_aaas()+
     ylab(bquote('log'~CH[4]~ 'flux (mg C' ~m^-2~ day^-1*')'))+
   xlab('5cm soil temperature (°C)')+
  geom_point() +
  #stat_function(fun=function(x) aGS.BB1*exp(bGS.BB1*x), colour = "red")+
  #stat_function(fun=function(x) aGS.BB2*exp(bGS.BB2*x), colour = "darkblue")+
    ggtitle("b.) Growing season")+
  theme_bw()+
    theme(legend.position = "none",
          axis.text = element_text(size = 12),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_blank())

TS.BB1.modNGS <-lm(logCH4_mgC~TS.5_mean, data = BB1.NGS)
MASS::boxcox(TS.BB1.modNGS)
summary(TS.BB1.modNGS)
RMSE.TS.BB1 <- sqrt(mean(residuals(TS.BB1.modNGS)^2))

TS.BB2.modNGS <-lm(logCH4_mgC~TS.5_mean, data = BB2.NGS)
MASS::boxcox(TS.BB2.modNGS)
summary(TS.BB2.modNGS)
RMSE.TS.BB2 <- sqrt(mean(residuals(TS.BB2.mod)^2))

Temp.logCH4NGS<- Flux.Env.Ngf %>% #don't need to log transform CH4? 
         filter(#logCH4_mgC > 2,
                Period == "NGS") %>%
  ggplot(., aes(TS.5_mean,logCH4_mgC, color= Site)) +
          scale_color_aaas()+
     ylab(bquote('log F'~CH[4]~ '(mg C' ~m^-2~ day^-1*')'))+
   xlab('5cm soil temperature (°C)')+
  geom_point() +
  #stat_function(fun=function(x) a.NGSBB1*exp(b.NGSBB1*x), colour = "red")+
  #stat_function(fun=function(x) a.NGSBB2*exp(b.NGSBB2*x), colour = "darkblue")+
    ggtitle("c.) Non-growing season")+
  theme_bw()+
    theme(axis.text = element_text(size = 12),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_blank(),
          legend.title = element_text(size=14),
          legend.text = element_text(size= 14))

ggarrange(Temp.logCH4, Temp.logCH4GS, Temp.logCH4NGS, nrow = 1, ncol = 3, common.legend = TRUE, widths = c(1, .9, .9))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/CH4temp.tiff", width = 8, height = 4, device='tiff', dpi=300)


tiff(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/CH4TS.tiff", width =900, height = 300) # The height of the plot in inches
grid.arrange(cbind(ggplotGrob(Temp.logCH4), ggplotGrob(Temp.logCH4GS), ggplotGrob(Temp.logCH4NGS), size = "last"))
dev.off()


```

```{r modelling WTH using Turetsky equation}
#Turetsky WTH model:
# FCH4 = estimated maximum FCH4 at the optimal WTH * [exp -0.5 * (WTH - estimated optimal water table position for FCH4^2/width of the WT amplitude^2)]
library(qpcR)
BB1 <- BB1 %>% drop_na(WTH._mean)

nlsfit.annualBB1.CH4.WTH <- nls(logCH4_mgC ~ a * exp(-0.5 * (((BB1$WTH._mean - b)^2)/(c^2))), data = BB1, start = list(a = 0.1, b = 0.1, c = 0.1))
summary(nlsfit.annualBB1.CH4.WTH)

nlsfit.annualBB1.CH4.WTH <- nls(CH4_mgC ~ a * exp(-0.5 * (((BB1$WTH._mean - b)^2)/(c^2))), data = BB1, start = list(a = -1, b = -1, c = -1))
qpcR::RMSE(nlsfit.annualBB1.CH4.WTH, which = NULL)


coefs.annualBB1.CH4.WTH <- coef(nlsfit.annualBB1.CH4.WTH)
coefs.annualBB1.CH4.WTH

a.1.CH4.WTH<- 4.656396
b.1.CH4.WTH<- -7.030082
c.1.CH4.WTH<- 15.803311 

plot(BB1$WTH._mean, BB1$logCH4_mgC)
lines(BB1$WTH._mean, coefs.annualBB1.CH4.WTH[["a"]]*exp(-0.5 * (((BB1$WTH._mean - coefs.annualBB1.CH4.WTH[["b"]])^2)/(coefs.annualBB1.CH4.WTH[["c"]]^2))))

#BB2
BB2 <- BB2 %>% drop_na(WTH._mean)

nlsfit.annualBB2.CH4.WTH <- nls(logCH4_mgC ~ a * exp(-0.5 * (((BB2$WTH._mean - b)^2)/(c^2))), data = BB2, start = list(a = 0.1, b = 0.1, c = 0.1))

nlsfit.annualBB2.CH4.WTH <- nls(CH4_mgC ~ a * exp(-0.5 * (((BB2$WTH._mean - b)^2)/(c^2))), data = BB2, start = list(a = -1, b = -1, c = -1))
summary(nlsfit.annualBB2.CH4.WTH)
coefs.annualBB2.CH4.WTH <- coef(nlsfit.annualBB2.CH4.WTH)
coefs.annualBB2.CH4.WTH

a.2.CH4.WTH <-4.424348
b.2.CH4.WTH <--30.925333
c.2.CH4.WTH <-49.287712 

plot(BB2$WTH._mean, BB2$logCH4_mgC)
lines(BB2$WTH._mean, coefs.annualBB2.CH4.WTH[["a"]]*exp(-0.5 * (((BB2$WTH._mean - coefs.annualBB2.CH4.WTH[["b"]])^2)/(coefs.annualBB2.CH4.WTH[["c"]]^2))))

```


__BB1__ 

```{r BB1 model}
#####RUN THESE  WITH THE CH4 GPP CHUNK BELOW INSTEAD OF HERE!!
TS.BB1.mod <- lm(formula = logCH4_mgC ~ TS.5_mean, data = BB1)
WTH.BB1.mod <- lm(formula = logCH4_mgC ~ WTH._mean, data = BB1)
model.2.both.BB1 <- lm(logCH4_mgC ~TS.5_mean * WTH._mean, data = BB1)

model.sel(model.1.both.BB1, model.2.both.BB1, WTH.BB1.mod, TS.BB1.mod, model.BB1.full, mod.BB1.2 )
plot(allEffects(model.5))

summary(mod.BB1.2)
summary(model.6)
anova(model.2, model.1)

RMSE.BB1 <- sqrt(mean(residuals(model.2)^2))

BB1.model <- BB1 %>% dplyr::select(logCH4_mgC, TS.5_mean, WTH._mean, TS.5_mean, GPP_f)

#Stepwise regression
full.model<-(lm(logCH4_mgC ~ ., data = BB1.model)

step.model <- stepAIC(full.model, direction = "backward")
stepAIC(full.model)

leaps<-regsubsets(logCH4_mgC ~ TS.5_mean * WTH._mean + TS.5_mean * GPP_f, data=BB1,nbest=5)
# view results
summary(leaps)
plot(leaps,scale="r2")



```


__BB2__


```{r BB2 model reln between CH4 and Temp and WTH}
library(MASS)

model.1.both.BB2 <- lm(logCH4_mgC  ~TS.5_mean + WTH._mean, data = BB2)
model.2.both.BB2 <- lm(logCH4_mgC ~TS.5_mean * WTH._mean, data = BB2)

model.3 <- lm(logCH4_mgC  ~TS.5_mean + WTH._mean, data = BB2.GS)
model.4 <- lm(logCH4_mgC ~TS.5_mean * WTH._mean, data = BB2.GS)

model.5 <- lm(logCH4_mgC  ~TS.5_mean + WTH._mean, data = BB2.NGS)
model.6 <- lm(logCH4_mgC ~TS.5_mean * WTH._mean, data = BB2.NGS)
#model.3 <- lm(logCH4_mgC  ~ TS.5_mean + poly(WTH._mean, 2, raw = TRUE) , data = BB2) 
#model.4 <- lm(logCH4_mgC  ~ TS.5_mean * poly(WTH._mean, 2, raw = TRUE) , data = BB2) 
#model.5 <- lm(logCH4_mgC  ~ TS.5_mean + poly(WTH._mean, 3, raw = TRUE) , data = BB2) 


model.sel(model.1.both.BB2, model.2.both.BB2, WTH.BB2.mod, TS.BB2.mod )
model.sel(model.1, model.2, model.3, model.4, model.5, model.6)
plot(allEffects(model.5))

summary(model.6) 
anova(model.2, model.1)


MASS::boxcox(model.6, lambda = seq(-1,1, length=10))

```


- "When the water table is high, CH4 emissions are not regulated by WTD, particularly in vascular plant dominated wetlands... transport of CH4 from sediment to atmosphere via aerenchyma is inhibited by the inundation of AGB of plants" (REF) - from Zhu et al., 2020

```{r compare BB1 and BB2 CH4, figures-side, fig.show="hold", out.width="50%"}
ggplot(BB1, aes(WTH._mean, logCH4_mgC)) +
  geom_point(aes(color = TS.5_mean)) +
        #geom_line(aes(x = WTH._mean, y = predictedlogCH4))+
  scale_color_gradient(low = "light blue", high = "dark blue")+
  #stat_smooth(method = lm, formula = y ~ x+c)+
  xlab("WTH (cm)")+
ylab(bquote('log'~CH[4]~ 'flux (mg C' ~m^-2~ day^-1*')'))+
  ggtitle("BB1")+
  theme_bw()


(CH4.model2 <- BB2  %>%
  ggplot(., aes(TS.5_mean, logCH4_mgC)) +
  geom_point(aes(color = WTH._mean)) +
      #geom_smooth(aes(x = WTH._mean, y = predictedlogCH4))+
          #geom_smooth(aes(x = WTH._mean, y = logCH4_mgC))+
  scale_color_gradient(low = "light blue", high = "dark blue",  limits = c(-40,20))+
  #stat_function(fun=function(x) a.BB2*exp(b.BB2*x))+
    stat_smooth(method = "lm", se = FALSE, size = 0.5, color = "black")+
             scale_y_continuous(limits = c(0,5))+
  #stat_smooth(method = 'lm', formula = y ~ x)+
  xlab("Soil temperature")+
ylab(bquote('lnFCH4 (mg C' ~m^-2~ day^-1*')'))+
  ggtitle("a")+
  theme_bw()+
    theme(axis.text.x = element_text(size = 12),
          axis.title.x = element_text(size = 12),
          axis.text.y = element_text(size = 12),
          axis.title.y = element_text(size = 12)))

(CH4.model1 <- BB1 %>% filter(logCH4_mgC > 0) %>%
  ggplot(., aes(TS.5_mean, logCH4_mgC) ) +
  geom_point(aes(color = WTH._mean)) +
    geom_smooth(method = "lm",se = FALSE, size = 0.5, colour = "black")+
      #geom_smooth(aes(x = WTH._mean, y = predictedlogCH4))+
          #geom_smooth(aes(x = WTH._mean, y = logCH4_mgC))+
  scale_color_gradient(low = "light blue", high = "dark blue", ,  limits = c(-40,20))+
  #stat_function(fun=function(x) a.BB1*exp(b.BB1*x))+
         scale_x_continuous(limits = c(0,20))+
  #stat_smooth(method = 'lm', formula = y ~ x)+
  xlab("Soil temperature")+
ylab(bquote('lnFCH4 (mg C' ~m^-2~ day^-1*')'))+
  ggtitle("b")+
  theme_bw() +
    theme(axis.text.x = element_text(size = 12),
          axis.title.x = element_text(size = 12),
          axis.text.y = element_text(size = 12),
          axis.title.y = element_text(size = 12)))

(CH4.model3 <- Flux.Env.Ngf %>% filter(logCH4_mgC > 0) %>%
  ggplot(., aes(WTH._mean, TS.5_mean) ) +
  geom_point(aes(color = logCH4_mgC, size = , alpha  = 0.5)) +
  #scale_color_gradient(low = "yellow", high = "red")+
    scale_x_continuous(limits = c(-10,10))+
        scale_y_continuous(limits = c(0,20))+
  #stat_smooth(method = 'lm', formula = y ~ x)+
  xlab("WTH (cm)")+
ylab('Soil temperature')+
  ggtitle("b")+
  theme_bw() +
    theme())

ch4flux.test <- Flux.Env.Ngf %>% select(Site, CH4mgC_f,CH4_mgC, logCH4_mgC, TS.5_mean, WTH._mean) %>% filter(CH4mgC_f >0)
library(scatterplot3d)

with(ch4flux.test, scatterplot3d(TS.5_mean, WTH._mean, CH4mgC_f, color = as.numeric(Site), pch = 25))


ch4flux.test.BB1 <- ch4flux.test %>% filter(Site == "1" & logCH4_mgC >0)
ch4flux.test.BB2 <- ch4flux.test %>% filter(Site == "2"& logCH4_mgC >0)


p <- ggplot(ch4flux.test, aes(TS.5_mean, CH4_mgC, group = Site))
p + geom_point(aes(color = Site)) + facet_wrap(~ cut_number(WTH._mean, 9)) +scale_color_jco()+theme_bw()

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/CH4tempWTH.tiff", width = 6, height = 4, device='tiff', dpi=300)



ggarrange(CH4.model2, CH4.model1, nrow = 1, ncol = 2,common.legend = TRUE, widths = c(1,1))
ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/CH4tempWTH.tiff", width = 6, height = 4, device='tiff', dpi=300)


# Turetsky WTH CH4 response:
Pred.ch4 <- max(BB1$logCH4_mgC) * exp(-0.5 * (BB1$WTH._mean))
```

```{r}
#BB1
g<- expand.grid(TS.5_mean = seq(0, 25, 1), WTH._mean = seq(-20, 15, 2))
g$BB1 <- (1.79 + 0.14*(g$TS.5_mean) + 0.04*(g$WTH._mean) - 0.01*(g$TS.5_mean*g$WTH._mean))
wireframe(BB1~TS.5_mean*WTH._mean, data = g,
          scales = list(arrows = FALSE),
          drape = TRUE, colorkey = TRUE,
          screen = list(z = 70, x = -60))

(WvBB1<- wireframe(BB1~WTH._mean*TS.5_mean, data = g,
          scales = list(arrows = FALSE),
          drape = TRUE, colorkey = TRUE,
                     at=do.breaks(c(0,10),10),
          auto.key = TRUE,
          screen = list(z = 40, x = -50),
          xlab = list("WTH", rot = 30),
           ylab = list("Soil temperature", rot = -30),
          zlab = list("lnCH4", rot = 90),
          zlim = c(0, 10),
          par.settings = list(axis.line = list(col = 'transparent')),
          panel = function(...)
    {
      panel.wireframe(...)
      grid.text("CA-DBB", 0, 0.2, default.units = "native")
    }))

tiff(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/BB1surface.tiff", width =800, height = 500) # The height of the plot in inches
WvBB1
dev.off()


#BB2
h<- expand.grid(TS.5_mean = seq(0, 25, 1), WTH._mean = seq(-20, 15, 2))
h$BB2 <- (3.30 + 0.03*(h$TS.5_mean) - 0.02*(h$WTH._mean))
(wireframe(BB2~TS.5_mean*WTH._mean, data = h,
          scales = list(arrows = FALSE),
          #drape = TRUE, colorkey = TRUE,
          screen = list(z = 70, x = -60)))

(WvBB2<- wireframe(BB2~WTH._mean*TS.5_mean, data = h,
          scales = list(arrows = FALSE),
          drape = TRUE, colorkey = TRUE,
           at=do.breaks(c(0,10),10),
          auto.key = TRUE,
          screen = list(z = 40, x = -50),
          xlab = list("WTH", rot = 30),
           ylab = list("Soil temperature", rot = -30),
          zlab = list("lnCH4", rot = 90),
          zlim = c(0, 10),
          par.settings = list(axis.line = list(col = 'transparent')),
          panel = function(...)
    {
      panel.wireframe(...)
      grid.text("CA-DB2", 0, 0.2, default.units = "native")
    }))

tiff(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/BB2surface.tiff", width =800, height = 500) # The height of the plot in inches
WvBB2
dev.off()


```



### CH4 and CO2 relationships

__CH4 emissions and C sequestration__

- need to ask whether GPP is a significant driving factor for CH4 emissions (Fig 2 from Hemes paper)

- It seems that for a given value of NEE <0, BB1 produces more CH4 than BB1 - maybe this could mean that at BB1, WTH is more important than the influence of vascular veg....  At BB2, more vascular vegetation, driven by lower water tables, means that CH4 emissions are lower. This is surprising because I would've thought that more labile substrate from vascular veg --> more ch4 emissions, considering I dont think the SWC is limiting...

- Below both sites are plotted differently and it looks like there are differences between their relationships.

```{r CH4 emissions and C sequestration}
Flux.Env.GF.NGF <- right_join(Flux.Env.Ngf, Flux.Env)
```

Sequestering more CO2  --> higher CH4 fluxes at BB2 - potentially due to labile substrate input?

```{r CH4 emissions and C sequestration BB1 and BB2 sep, figures-side, fig.show="hold", out.width="50%"}

Flux.Env.GF.NGF <- right_join(Flux.Env.Ngf, Flux.Env)
 tmp <- Flux.Env.GF.NGF %>% dplyr::select(Site, GPPgC_f) %>% filter(Site=="CA-DB2")

BB1GFNGF <- Flux.Env.GF.NGF %>% filter(Site == "CA-DBB") %>% mutate (GPPgC_f = GPPgC_f + 0.6) #%>% mutate(logGPPgC_f = log(GPPgC_f))
BB2GFNGF <- Flux.Env.GF.NGF %>% filter(Site == "CA-DB2") %>% mutate (GPPgC_f = GPPgC_f + 0.75)
BB1GFNGF.GS <- BB1GFNGF %>% filter(Period =="GS")
BB2GFNGF.GS <- BB2GFNGF %>% filter(Period =="GS")
BB1GFNGF.NGS <- BB1GFNGF %>% filter(Period =="NGS")
BB2GFNGF.NGS <- BB2GFNGF %>% filter(Period =="NGS")

CH4GPP <- full_join(BB1GFNGF, BB2GFNGF)

#Annual
(CH4.Cseq.p <-CH4GPP %>% 
       #filter(logCH4_mgC > 2) %>%
  ggplot(., aes(GPPgC_f, logCH4_mgC, color = Site)) +
  geom_point()+
   #geom_smooth(method = "lm", aes(colour = Site)) +
    #scale_x_log10()+
  #scale_colour_manual(values = c("#0072B2", "#D55E00")) +
  xlab(bquote('GPP (g C' ~m^-2~ day^-1*')'))+
    ylab(bquote('' ~lnCH[4]~ ' (g C' ~m^-2~ day^-1*')'))+
    #scale_x_continuous(limits = c(- 2))+
    scale_color_aaas()+
    ggtitle("Annual")+
  theme_bw()+ 
    theme(axis.title = element_text(size = 15),
          axis.text = element_text(size = 14)))

CH4GPP.mod <- aov(logCH4_mgC~log(GPPgC_f)*Site, CH4GPP)
summary(CH4GPP.mod)
```

```{r BB1 models with GPP}
options(na.action = "na.omit")
TS.BB1.mod <- lm(formula = logCH4_mgC ~ TS.5_mean, data = BB1GFNGF)
WTH.BB1.mod <- lm(formula = logCH4_mgC ~ WTH._mean, data = BB1GFNGF)
CH4.GPP.BB1 <- lm(logCH4_mgC~GPPgC_f, data = BB1GFNGF)

model.2.both.BB1 <- lm(logCH4_mgC ~TS.5_mean * WTH._mean, data = BB1GFNGF)
model.3.both.BB1 <- lm(logCH4_mgC ~TS.5_mean + WTH._mean, data = BB1GFNGF)

#BB1GFNGF.allmod <- BB1GFNGF %>% dplyr::select(logCH4_mgC, TS.5_mean, WTH._mean, GPPgC_f)

#BB1.modAll <- lm(logCH4_mgC ~ ., data = BB1GFNGF.allmod)

summary(TS.BB1.mod)

FullCH4.BB1 <- lm(logCH4_mgC~log(GPPgC_f)*TS.5_mean * WTH._mean, data = BB1GFNGF)
#CH4.GPP.BB1.2 <- lm(logCH4_mgC~log(GPPgC_f)*TS.5_mean + WTH._mean, data = BB1GFNGF)
#CH4.GPP.BB1.2 <- lm(logCH4_mgC~log(GPPgC_f)*TS.5_mean, data = BB1GFNGF)

allEffects(FullCH4.BB1)

mod.2 <- lm(logCH4_mgC~TS.5_mean + (TS.5_mean:WTH._mean), data = BB1GFNGF)
summary(mod.2)


m<- ols_step_best_subset(FullCH4.BB1)
n<- ols_step_all_possible(FullCH4.BB1, details=TRUE)

try <- lm(logCH4_mgC~log(GPPgC_f)+WTH._mean +log(GPPgC_f):TS.5_mean, data = BB1GFNGF)
summary(try)
      

step <- stepAIC(FullCH4.BB1, direction = "backward", trace = FALSE)
step$anova

model.sel(TS.BB1.mod, WTH.BB1.mod, CH4.GPP.BB1, model.2.both.BB1, model.3.both.BB1)
summary(model.3.both.BB1)

CH4GPP.BB2 <- lm(logCH4_mgC~log(GPPgC_f), data = BB2GFNGF)

summary(CH4GPP.BB2)

CH4GPP.BB2.1 <- lm(logCH4_mgC~log(GPPgC_f)*TS.5_mean, data = BB2GFNGF)
summary(CH4GPP.BB2.1)

#summary(CH4.GPPBB1)
(CH4.Cseq.pBB1 <-BB1GFNGF %>% 
  ggplot(., aes(GPPgC_f, logCH4_mgC)) +
  geom_point(aes(color = TS.5_mean))+
    #geom_smooth(method = "lm")+
      scale_color_gradient(low = "yellow", high = "red", limits = c(0, 25))+
        #scale_y_continuous(limits = c(2,5.5))+
            scale_x_continuous(limits = c(0,6))+
    #scale_x_log10()+
  xlab(bquote('GPP (g C' ~m^-2~ day^-1*')'))+
    ylab(bquote('' ~lnFCH[4]~ ' (g C' ~m^-2~ day^-1*')'))+
    ggtitle("BB1")+
  theme_bw())
```

```{r BB2 MODELS WITH GPP}
library(olsrr)

TS.BB2.mod <- lm(formula = logCH4_mgC ~ TS.5_mean, data = BB2GFNGF)
WTH.BB2.mod <- lm(formula = logCH4_mgC ~ WTH._mean, data = BB2GFNGF)
CH4.GPP.BB2 <- lm(logCH4_mgC~log(GPPgC_f), data = BB2GFNGF)

model.2.both.BB2 <- lm(logCH4_mgC ~TS.5_mean * WTH._mean, data = BB2GFNGF)
model.3.both.BB2 <- lm(logCH4_mgC ~TS.5_mean + WTH._mean + log(GPPgC_f), data = BB2GFNGF)
model.3.both.BB2$coefficients

#model.3 <- lm(logCH4_mgC~log(GPPgC_f)*TS.5_mean, data = BB2GFNGF)
#model.4 <- lm(logCH4_mgC~log(GPPgC_f)+TS.5_mean, data = BB2GFNGF)
#model.3.both.BB2 <- lm(logCH4_mgC ~TS.5_mean + WTH._mean, data = BB2GFNGF)

FullCH4.BB2 <- lm(logCH4_mgC~log(GPPgC_f)*TS.5_mean * WTH._mean, data = BB2GFNGF)
#FullCH4.BB2.2 <- lm(logCH4_mgC~log(GPPgC_f)*TS.5_mean + WTH._mean, data = BB2GFNGF)

summary(model.3.both.BB2)

model.sel(TS.BB2.mod, WTH.BB2.mod, CH4.GPP.BB2, model.2.both.BB2, model.3.both.BB2)

j <- ols_step_all_possible(FullCH4.BB2, details=TRUE)

k <- ols_step_best_subset(FullCH4.BB2, details = TRUE)
step<-stepAIC(FullCH4.BB2)
step$coefficients
summary(step)
model.sel(model.2.both.BB2, model.3.both.BB2, FullCH4.BB2, FullCH4.BB2.2)

ols_coll_diag(FullCH4.BB2)


#summary(CH4.GPPBB2)


CH4GPP.BB1.GS <- lm(logCH4_mgC~log(GPPgC_f), data = BB1GFNGF.GS)
plot(CH4GPP.BB1.GS)
boxcox(CH4GPP.BB1.GS)
summary(CH4GPP.BB1.GS)

CH4GPP.BB2.GS <- lm(logCH4_mgC~log(GPPgC_f), data = BB2GFNGF.GS)
plot(CH4GPP.BB2.GS)
boxcox(CH4GPP.BB2.GS)
summary(CH4GPP.BB2.GS)

CH4GPP.BB1.NGS <- lm(logCH4_mgC~log(GPPgC_f), data = BB1GFNGF.NGS)
plot(CH4GPP.BB1.NGS)
boxcox(CH4GPP.BB1.NGS)
summary(CH4GPP.BB1.NGS)

CH4GPP.BB2.NGS <- lm(logCH4_mgC~log(GPPgC_f), data = BB2GFNGF.NGS)
plot(CH4GPP.BB2.NGS)
boxcox(CH4GPP.BB2.NGS)
summary(CH4GPP.BB2.NGS)

ggarrange(CH4.Cseq.pBB1, CH4.Cseq.pBB2,  common.legend = TRUE)

CH4GPP.temp <- aov(logCH4_mgC ~ GPPgC_f * TS.5_mean * WTH._mean*Site, data = CH4GPP)
summary(CH4GPP.temp)
```


### FACET PLOTS FOR SINGLE RESPONSE VARIABLE
```{r CH4}
# Temperature response 
(Temp.logCH4<- Flux.Env.Ngf %>%  
         #filter(logCH4_mgC > 2) %>%
  ggplot(., aes(TS.5_mean,logCH4_mgC, color= Site)) +
           #scale_shape_manual(values = c(1,15))+
   scale_color_jco()+
     ylab(bquote('lnFCH4(mg C' ~m^-2~ day^-1*')'))+
   xlab('5cm soil temperature (°C)')+
  geom_point(aes(), size = 1) +
   geom_smooth(method = "lm", se = FALSE, size = 0.5) +
  #stat_function(fun=function(x) a.BB1*exp(b.BB1*x), color = "#EFC000FF")+
  #stat_function(fun=function(x) a.BB2*exp(b.BB2*x), color ="#0073C2FF" )+
    ggtitle("a")+
  theme_bw()+
   theme(legend.position = "none",
         axis.text = element_text(size = 14),
          axis.title.x = element_text(size = 14),
          axis.title.y = element_blank()))

# Water table response
func.bb1 <- function(x) a.1.CH4.WTH*exp(-0.5 * ((x - b.1.CH4.WTH)^2)/((c.1.CH4.WTH)^2))
func.bb2 <- function(x) a.2.CH4.WTH*exp(-0.5 * ((x - b.2.CH4.WTH)^2)/((c.2.CH4.WTH)^2))

(WTH.logCH4<- Flux.Env.Ngf %>% #don't need to log transform CH4? 
  #filter(WTH._mean > -20.0) %>%
         #logCH4_mgC > 2) %>%
  ggplot(., aes(WTH._mean,logCH4_mgC,  color= Site)) +
        #scale_shape_manual(values = c(1,15))+
          scale_color_jco()+
     ylab(bquote('log'~CH[4]~ 'flux (mg C' ~m^-2~ day^-1*')'))+
   xlab('WTH (cm)')+
  geom_point(aes(), size = 1) +
    stat_function(fun=func.bb1, xlim = c(-13, 13), color ="#EFC000FF") +
        stat_function(fun=func.bb2, color = "#0073C2FF") +
    ggtitle("b") +
  theme_bw()+
    theme(legend.position = "none",
          axis.text = element_text(size = 14),
          axis.title.x = element_text(size = 14),
          axis.text.y = element_blank(),
          axis.title.y = element_blank()))


#GPP
(CH4.Cseq.p <-CH4GPP %>% 
       #filter(logCH4_mgC > 2) %>%
  ggplot(., aes(log(GPPgC_f), logCH4_mgC, color = Site)) +
  geom_point(aes(), size = 1)+
    scale_x_continuous(limits = c(-1,2))+
    #scale_shape_manual(values = c(1,15))+
   geom_smooth(method = "lm", se = FALSE, aes(colour = Site), size = 0.5) +
    #scale_x_log10()+
  #scale_colour_manual(values = c("#0072B2", "#D55E00")) +
  xlab(bquote('lnGPP (g C' ~m^-2~ day^-1*')'))+
    ylab(bquote('' ~lnCH[4]~ ' (g C' ~m^-2~ day^-1*')'))+
    #scale_x_continuous(limits = c(- 2))+
    scale_color_jco()+
    ggtitle("c")+
  theme_bw()+ 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 14),
          axis.text.y = element_blank(),
          axis.title.y = element_blank(),
          legend.text = element_text(size = 13),
          legend.title = element_text (size = 13)))

(ch4.singleresponse <- ggarrange(Temp.logCH4,WTH.logCH4,CH4.Cseq.p, ncol = 3, common.legend = TRUE, widths = c(1.05, 1, 1), align = "h"))
annotate_figure(ch4.singleresponse, left = text_grob(bquote('lnFCH4 (mg C' ~m^-2~ day^-1*')'), rot =90, size = 14))
ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/CH4SRvars.tiff", width = 7.75, height = 4, device='tiff', dpi=300)

```

```{r CO2}
#Temperature response


BB1.int <- -2
BB2.int <- -.9
BB1.coef <- 0.12
BB2.coef <- 0.09


##LN RECO
(ER.TS5.P <- Flux.Env %>%
  #filter(TS.5_mean > '0') %>%
  ggplot(., aes(TS.5_mean, lnRECO, color= Site)) +
       scale_color_jco()+
   xlab('5cm Soil temperature (°C)')+
   ylab(bquote('lnRECO (g C' ~m^-2~ day^-1*')'))+
    geom_smooth(method = "lm", se = FALSE, size = 0.5) +
   #scale_y_continuous(limits = c(0,3))+
  geom_point()+
  #stat_function(fun=function(x) BB1.int+(BB1.coef*x), colour = "#EFC000FF")+
  #stat_function(fun=function(x) BB2.int+(BB2.coef*x), colour = "#0073C2FF")+
    ggtitle("a")+
  theme_bw()+
   theme(legend.position=c(.15, 0.85),
          axis.text = element_text(size = 14),
          axis.title = element_text(size = 15)))#,
         #axis.title.y = element_blank(),
         #axis.text.y = element_blank()))

ER.TS5.P

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/lNRECOtemp.tiff", width = 4, height = 4, device='tiff', dpi=300)

#Water table response
(ER.WTH.P <- Flux.Env %>%
 #filter(WTH._mean > -20.0) %>%
  ggplot(., aes(WTH._mean, lnRECO, color= Site)) +
       scale_color_jco()+
   xlab('WTH(cm)')+
   ylab(bquote('lnRECO (g C' ~m^-2~ day^-1*')'))+
       #scale_y_continuous(limits = c(0,3))+
  geom_point()+
   geom_smooth(method = "lm", se = FALSE, size = 0.5) + 
    ggtitle("b")+
  theme_bw()+
   theme(legend.position = "none", axis.text = element_text(size = 14),
          axis.title = element_text(size = 15)))#,
        #axis.title.y = element_blank(),
         #axis.text.y = element_blank()))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/lnCO2WTH.tiff", width = 4, height = 4, device='tiff', dpi=300)

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/CO2WTH.tiff", width = 4, height = 4, device='tiff', dpi=300)


(RECO.SR <- ggarrange(ER.TS5.P, ER.WTH.P, nrow = 1, ncol = 2, common.legend = TRUE, widths = c(1, 1), align = "h"))
#annotate_figure(RECO.SR, left = text_grob(bquote('lnRECO (g C' ~m^-2~ day^-1*')'), rot =90))
ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/CO2SRvars.tiff", width = 6, height = 3, device='tiff', dpi=300)


(GPP.TS5.P <- Flux.Env %>%
  #filter(TS.5_mean > '0') %>%
  ggplot(., aes(TS.5_mean, GPP_f, color= Site)) +
       scale_color_aaas()+
   xlab('5cm Soil temperature (°C)')+
   #ylab(bquote('RECO (g C' ~m^-2~ day^-1*')'))+
   scale_y_continuous(limits = c(0,3))+
  geom_point()+
  #stat_function(fun=function(x) a.annBB1*exp(b.annBB1*x), colour = "red")+
  #stat_function(fun=function(x) a.annBB2*exp(b.annBB2*x), colour = "darkblue")+
    ggtitle("a")+
  theme_bw()+
   theme(legend.position = "none",
          axis.text = element_text(size = 12),
          axis.title.x = element_text(size = 12),
         axis.title.y = element_blank()))

(GPP.WTH.P <- Flux.Env %>%
 filter(WTH._mean > -20.0) %>%
  ggplot(., aes(WTH._mean, GPP_f, color= Site)) +
       scale_color_aaas()+
   xlab('WTH(cm)')+
   ylab(bquote('Ecosystem respiration (g C' ~m^-2~ day^-1*')'))+
       scale_y_continuous(limits = c(0,3))+
  geom_point()+
   #geom_smooth(method = "lm", se = FALSE) + 
    ggtitle("b")+
  theme_bw()+
   theme(legend.position = "none", axis.text = element_text(size = 12),
          axis.title.x = element_text(size = 12),
         axis.title.y = element_blank(),
         axis.text.y = element_blank()))

```

```{r calculate missing values}
missing.BB2 <- read.csv('/Users/marionnyberg/Google\ Drive/Micromet\ Lab/Projects/2019-Burns\ Bog\ 2/Flux-tower/flux_data/BB2_L2.csv') %>% dplyr::select(DATE, co2_flux, ch4_flux)
missing.BB2$Timestamp <- as.POSIXct(missing.BB2$DATE, format = "%Y-%m-%d %H:%M:%S", tz="UTC")
missing.BB2 <- missing.BB2 %>% filter(Timestamp >= '2020-01-01 00:00:00' & Timestamp < '2021-01-01 00:00:00')

BB2.NAs.co2 <- na.omit(missing.BB2$co2_flux)

BB2.obs <- 17568
BB2.noNAS <- 11611
co2_missing <- ((BB2.obs-BB2.noNAS)/BB2.obs)*100

BB2.NAs.ch4 <- na.omit(missing.BB2$ch4_flux)

BB2.noNAS.ch4 <- 9238
ch4_missing <- ((BB2.obs-BB2.noNAS.ch4)/BB2.obs)*100


missing.BB1 <- read.csv('/Users/marionnyberg/Google\ Drive/Micromet\ Lab/Projects/2014-Burns\ Bog/Flux-tower/flux_data/BB_L2.csv')%>% dplyr::select(DATE, co2_flux, ch4_flux)

missing.BB1$Timestamp <- as.POSIXct(missing.BB1$DATE, format = "%Y-%m-%d %H:%M:%S", tz="UTC")
missing.BB1 <- missing.BB1 %>% filter(Timestamp >= '2020-01-01 00:00:00' & Timestamp < '2021-01-01 00:00:00')

BB1.NAs.co2 <- na.omit(missing.BB1$co2_flux)

BB1.obs <- 17568
BB1.noNAS <- 10150
co2_missing.1 <- ((BB1.obs-BB1.noNAS)/BB1.obs)*100

BB1.NAs.ch4 <- na.omit(missing.BB1$ch4_flux)

BB1.noNAS.ch4 <- 7939
ch4_missing.1 <- ((BB1.obs-BB1.noNAS.ch4)/BB1.obs)*100

```

```{r check for colinearity}
colin.subset <- Flux.Env.GF.NGF %>% dplyr::select(logCH4_mgC, WTH._mean, TS.5_mean, GPP_f)
colin.subset$GPP_f <- log(colin.subset$GPP_f)
colin.m <- lm(logCH4_mgC~., colin.subset)
vif(colin.m)
cor(colin.subset, use = "complete.obs")
```

```{r calculate energy balace closure}
###BB2
EB.BB2 <- read.csv('/Users/marionnyberg/Google\ Drive/Micromet\ Lab/Projects/2019-Burns\ Bog\ 2/Flux-tower/flux_data/BB2_L3.csv') %>% dplyr::select(DATE, H, LE, NR, G)
EB.BB2$Timestamp <- as.POSIXct(EB.BB2$DATE, format = "%Y-%m-%d %H:%M:%S", tz="UTC")
EB.BB2 <- EB.BB2 %>% filter(Timestamp >= '2020-01-01 00:00:00' & Timestamp < '2021-01-01 00:00:00')
EB.BB2$jday <- yday(EB.BB2$Timestamp)


EB.BB2.daily <- EB.BB2 %>% dplyr::select(jday, H, LE, NR, G) %>%
  ddply(c("jday"), summarise,
      H = mean(H, na.rm = TRUE),
      LE = mean(LE, na.rm = TRUE),
      NR = mean(NR, na.rm = TRUE),
      G = mean(G, na.rm = TRUE))


Ebal_denominator <- EB.BB2$NR-EB.BB2$G

Ebal_numerator <- EB.BB2$H+EB.BB2$LE

plot(x = Ebal_denominator, y = Ebal_numerator, xlab="Rn-G",ylab="LE+H")


# calculate EB using slope to fit
a<-round(coef(lm(Ebal_numerator~Ebal_denominator))[2],digits=2) #coef(lm(y~x))[2] is the slope of the regression
b<-round(coef(lm(Ebal_numerator~Ebal_denominator))[1],digits=2)   
r2<-round(summary(lm(Ebal_numerator~Ebal_denominator))$ r.squared,digits=2)

lm_eq<-paste0("y=",a,"x",ifelse(b>0,"+",""),b)
R2<-bquote(R^2 == .(r2)) 

plot(x = Ebal_denominator, y = Ebal_numerator, xlab="Rn-G",ylab="LE+H")
abline(0,1)
abline(lm(Ebal_numerator~Ebal_denominator),col='grey',lty=2)
mtext( lm_eq,side=3,line=-2,at=200,cex=0.9)
mtext(R2,side=3,line=-3,at=200,cex=0.9)


Ebal_denominator.daily <- EB.BB2.daily$NR-EB.BB2.daily$G

Ebal_numerator.daily <- EB.BB2.daily$H+EB.BB2.daily$LE

plot(x = Ebal_denominator.daily, y = Ebal_numerator.daily, xlab="Rn-G",ylab="LE+H")


# calculate EB using slope to fit DAILY
a<-round(coef(lm(Ebal_numerator.daily~Ebal_denominator.daily))[2],digits=2) #coef(lm(y~x))[2] is the slope of the regression
b<-round(coef(lm(Ebal_numerator.daily~Ebal_denominator.daily))[1],digits=2)   
r2<-round(summary(lm(Ebal_numerator.daily~Ebal_denominator.daily))$ r.squared,digits=2)

lm_eq<-paste0("y=",a,"x",ifelse(b>0,"+",""),b)
R2<-bquote(R^2 == .(r2)) 

plot(x = Ebal_denominator.daily, y = Ebal_numerator.daily, xlab="Rn-G",ylab="LE+H")
#abline(0,1)
abline(lm(Ebal_numerator.daily~Ebal_denominator.daily),col='grey',lty=2)
mtext( lm_eq,side=3,line=-2,at=200,cex=0.9)
mtext(R2,side=3,line=-3,at=200,cex=0.9)



###BB1

EB.BB1 <- read.csv('/Users/marionnyberg/Google\ Drive/Micromet\ Lab/Projects/2014-Burns\ Bog/Flux-tower/flux_data/BB_L3.csv') %>% dplyr::select(DATE, H, LE, NR, G)
EB.BB1$Timestamp <- as.POSIXct(EB.BB1$DATE, format = "%Y-%m-%d %H:%M:%S", tz="UTC")
EB.BB1 <- EB.BB1 %>% filter(Timestamp >= '2020-01-01 00:00:00' & Timestamp < '2021-01-01 00:00:00')
EB.BB1$jday <- yday(EB.BB1$Timestamp)


EB.BB1.daily <- EB.BB1 %>% dplyr::select(jday, H, LE, NR, G) %>%
  ddply(c("jday"), summarise,
      H = mean(H, na.rm = TRUE),
      LE = mean(LE, na.rm = TRUE),
      NR = mean(NR, na.rm = TRUE),
      G = mean(G, na.rm = TRUE))

Ebal_denominator.daily <- EB.BB1.daily$NR-EB.BB1.daily$G

Ebal_numerator.daily <- EB.BB1.daily$H+EB.BB1.daily$LE

plot(x = Ebal_denominator.daily, y = Ebal_numerator.daily, xlab="Rn-G",ylab="LE+H")


# calculate EB using slope to fit DAILY
a<-round(coef(lm(Ebal_numerator.daily~Ebal_denominator.daily))[2],digits=2) #coef(lm(y~x))[2] is the slope of the regression
b<-round(coef(lm(Ebal_numerator.daily~Ebal_denominator.daily))[1],digits=2)   
r2<-round(summary(lm(Ebal_numerator.daily~Ebal_denominator.daily))$ r.squared,digits=2)

lm_eq<-paste0("y=",a,"x",ifelse(b>0,"+",""),b)
R2<-bquote(R^2 == .(r2)) 

plot(x = Ebal_denominator.daily, y = Ebal_numerator.daily, xlab="Rn-G",ylab="LE+H")
#abline(0,1)
abline(lm(Ebal_numerator.daily~Ebal_denominator.daily),col='grey',lty=2)
mtext( lm_eq,side=3,line=-2,at=200,cex=0.9)
mtext(R2,side=3,line=-3,at=200,cex=0.9)


```

```{r figures for defence}
#WTH
(WTH.p.d <- ggplot(Env.input_data, aes(x = as.Date(jday, origin = as.Date("2020-01-01")), WTH._mean)) + #as.Date adds the month names into the plot
  #geom_ribbon(aes(ymin = WTH._min -1 , ymax = WTH._max+1), fill = "light grey")+
    geom_line(aes (color=Site)) +
   ylab("Water table height (cm)")+
  xlab("Month") +
   scale_x_date(date_breaks = "1 month", date_labels = "%b") +
          #scale_color_viridis(discrete = "TRUE", option = "D", begin = 0, end = 0.5)+
   scale_color_manual(values = c("orange1", "royalblue2")) +
  theme_bw() +
  theme(axis.text = element_text(size=14),
        axis.title = element_text(size=15),
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 15)))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/WTHdef.jpeg", width = 8, height = 4, device='jpeg', dpi=300)

#NEE
(NEEcum.d <-Flux.input_data %>% 
  ggplot(., aes(x = as.Date(jday, origin = as.Date("2020-01-01")), NEEcum, color = Site)) +
  geom_line(aes(color = Site))+
  ylab(bquote('Cumulative NEE (g C' ~m^-2~')'))+
  xlab("Month")+
    scale_x_date(date_breaks = "1 month", date_labels = "%b") +
    scale_color_manual(values = c("orange1", "royalblue2")) +
  theme_bw()+
   theme(axis.text = element_text(size=14),
      axis.title = element_text(size=15),
      legend.text = element_text(size = 13),
      legend.title = element_text(size = 13),
      legend.key.size = unit(1.5, "line")))#,
      #legend.justification=c(1.25, -1.8),
                        #legend.position=c(.9, 0.2)))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/NEEarrangedD.jpeg", width = 9, height = 7, device='jpeg', dpi=330)

#GPP
(GPPcum.D <-Flux.input_data %>% 
  ggplot(., aes(x = as.Date(jday, origin = as.Date("2020-01-01")), GPPcum_f, color = Site)) +
  geom_line()+
  ylab(bquote('Cumulative GPP (g C' ~m^-2~')'))+
  xlab("Month")+
     scale_x_date(date_breaks = "1 month", date_labels = "%b") +
        scale_color_manual(values = c("orange1", "royalblue2")) +
  theme_bw()+
    theme(axis.text = element_text(size=14),
      axis.title = element_text(size=15),
      axis.title.x = element_blank(),
      axis.text.x = element_blank(),
                        legend.position="none"))

(Recocum.D <-Flux.input_data %>% 
  ggplot(., aes(x = as.Date(jday, origin = as.Date("2020-01-01")), Recocum, color = Site)) +
  geom_line()+
  ylab(bquote('Cumulative RECO (g C' ~m^-2~')'))+
  xlab("Month")+
 scale_x_date(date_breaks = "1 month", date_labels = "%b") +
    scale_color_manual(values = c("orange1", "royalblue2"))+
 theme_bw()+
    theme(axis.text = element_text(size=14),
      axis.title = element_text(size=15),
      legend.position="none"))


(GPPER.arranged.D <- ggarrange(GPPcum.D, Recocum.D, nrow = 2, align = "v",common.legend = TRUE, heights=c(1, 1.2)))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/GPPER.jpeg", width = 9, height = 7, device='jpeg', dpi=300)


#RECO TS
(ER.TS5.P.d <- Flux.Env %>%
  ggplot(., aes(TS.5_mean, lnRECO, color= Site)) +
       scale_color_jco()+
   xlab('5cm Soil temperature (°C)')+
   ylab(bquote('lnRECO (g C' ~m^-2~ day^-1*')'))+
    geom_smooth(method = "lm", se = FALSE, size = 0.5) +
        scale_color_manual(values = c("orange1", "royalblue2"))+
  geom_point()+
  theme_bw()+
   theme(axis.text = element_text(size = 14),
          axis.title = element_text(size = 15)))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/lNRECOtempDef.jpeg", width = 7, height = 5, device='jpeg', dpi=300)

#Water table response
(ER.WTH.P <- Flux.Env %>%
  ggplot(., aes(WTH._mean, lnRECO, color= Site)) +
       scale_color_jco()+
   xlab('WTH(cm)')+
   ylab(bquote('lnRECO (g C' ~m^-2~ day^-1*')'))+
  geom_point()+
   geom_smooth(method = "lm", se = FALSE, size = 0.5) + 
            scale_color_manual(values = c("orange1", "royalblue2"))+
  theme_bw()+
   theme(axis.text = element_text(size = 14),
          axis.title = element_text(size = 15)))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/lnCO2WTHDef.jpeg", width = 7, height = 5, device='jpeg', dpi=300)

#GPP-PAR GS
(GS.LR <- GPP %>% filter(Period == "GS" & INCOMING_PAR > 10 & GPP_f > 0 & GPP_f < 20) %>%
  ggplot(., aes(INCOMING_PAR, GPP_f), group = Site) + geom_point(aes(color = Site))+
        scale_color_manual(values = c("orange1", "royalblue2"))+
    stat_function(fun=function(x) (a.GPP*x)*b.GPP/(a.GPP*x+b.GPP), colour = "royalblue2") +
  stat_function(fun=function(x) (a.GPP.2*x)*b.GPP.2/(a.GPP.2*x+b.GPP.2), colour = "orange1") +
        xlab(bquote('Incoming PAR ('*mu~'mol' ~m^-2~s^-1*')'))+
          ylab(bquote('GPP ('*mu~'mol'  ~m^-2~s^-1*')'))+
  ggtitle("Growing season")+
  theme(axis.text = element_text(size = 14),
          axis.title.x = element_text(size = 15),
         axis.title.y = element_text(size = 15))+
  theme_bw())

(NGS.lr <- GPP %>% filter(Period == "NGS" & INCOMING_PAR > 10 & GPP_f > 0 & GPP_f < 20) %>%
  ggplot(., aes(INCOMING_PAR, GPP_f), group = Site) + geom_point(aes(color = Site))+
        scale_color_manual(values = c("orange1", "royalblue2"))+
    stat_function(fun=function(x) (a.GPP.ngs*x)*b.GPP.ngs/(a.GPP.ngs*x+b.GPP.ngs), colour = "royalblue2") +
  stat_function(fun=function(x) (a.GPP.2ngs*x)*b.GPP.2ngs/(a.GPP.2ngs*x+b.GPP.2ngs), colour = "orange1") +
        xlab(bquote('Incoming PAR ('*mu~'mol' ~m^-2~s^-1*')'))+
          ylab(bquote('GPP ('*mu~'mol' ~m^-2~s^-1*')'))+
  ggtitle("Non-growing season") +
  theme(axis.title.y = element_blank(),
        axis.text = element_text(size = 14),
          axis.title.x = element_text(size = 15))+
         #axis.title.y = element_text(size = 12))+
  theme_bw())

(lightresposne.arranged <- ggarrange(GS.LR, NGS.lr, ncol = 2, common.legend = TRUE, align = "h", widths=c(1, 1)))


ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/LRarranged.jpeg", width = 6, height = 4, device='jpeg', dpi=330)

#NDVI
(NDVI.p <- ggplot(NDVI.new, aes(x = as.Date(jday, origin = as.Date("2020-01-01")), NDVI_lf)) + 
 geom_line(aes(colour = Site)) +
  ylab("NDVI")+
  xlab("Month") +
            scale_color_manual(values = c("orange1", "royalblue2"))+
    scale_x_date(date_breaks = "1 month", date_labels = "%b") +
  theme_bw()+
  theme(axis.text = element_text(size=14),
        axis.title = element_text(size=15)))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/NDVID.jpeg", width = 6.5, height = 4, device='jpeg', dpi=330)

#CH4 cumulative
(CH4cum.p.D <-Flux.input_data %>% 
  ggplot(., aes(x = as.Date(jday, origin = as.Date("2020-01-01")), CH4cum_f_RF_gC, color = Site)) +
  geom_line()+
  ylab(bquote('Cumulative FCH4 (g C' ~m^-2~')'))+
  xlab("Month")+
  scale_color_manual(values = c("orange1", "royalblue2"))+
     scale_x_date(date_breaks = "1 month", date_labels = "%b") +
  theme_bw()+
   theme(axis.text = element_text(size=14),
         axis.title = element_text(size=15),
         legend.title = element_text(size = 13),
         legend.text = element_text(size= 13)))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/CH4cumD.jpeg", width = 7.5, height = 4, device='jpeg', dpi=300)

#CH4 timeseries
(CH4.p.D <-Flux.input_data %>% 
  ggplot(., aes(x = as.Date(jday, origin = as.Date("2020-01-01")), CH4mgC_f_RF, color = Site)) +
  geom_line()+
  ylab(bquote('FCH4 (mg C' ~m^-2~')'))+
  xlab("Month")+
      scale_color_manual(values = c("orange1", "royalblue2"))+
 scale_x_date(date_breaks = "1 month", date_labels = "%b") +
 theme_bw()+
   theme(axis.text = element_text(size=14),
         axis.title = element_text(size=15)))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/CH4D.jpeg", width = 7.5, height = 4, device='jpeg', dpi=300)

#CH4TS
(Temp.logCH4D<- Flux.Env.Ngf %>%  
  ggplot(., aes(TS.5_mean,logCH4_mgC, color= Site)) +
     ylab(bquote('lnFCH4(mg C' ~m^-2~ day^-1*')'))+
    scale_color_manual(values = c("orange1", "royalblue2"))+
   xlab('5cm soil temperature (°C)')+
  geom_point(aes(), size = 1) +
   geom_smooth(method = "lm", se = FALSE, size = 0.5) +
    ggtitle("TS")+
  theme_bw()+
   theme(axis.text = element_text(size = 14),
          axis.title = element_text(size = 14)))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/CH4TSD.jpeg", width = 5, height = 4, device='jpeg', dpi=300)

#CH4 WTH
(WTH.logCH4D<- Flux.Env.Ngf %>% #don't need to log transform CH4? 
  ggplot(., aes(WTH._mean,logCH4_mgC,  color= Site)) +
        #scale_shape_manual(values = c(1,15))+
    scale_color_manual(values = c("orange1", "royalblue2"))+
    ylab(bquote('' ~lnFCH[4]~ ' (g C' ~m^-2~ day^-1*')'))+
   xlab('WTH (cm)')+
  geom_point(aes(), size = 1) +
    stat_function(fun=func.bb1, xlim = c(-13, 13), color ="royalblue2") +
        stat_function(fun=func.bb2, color = "orange1") +
    ggtitle("WTH") +
  theme_bw()+
    theme(axis.text = element_text(size = 14),
          axis.title = element_text(size = 14)))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/CH4WTH.jpeg", width = 5, height = 4, device='jpeg', dpi=300)


#CH4 GPP
(CH4.Cseq.p <-CH4GPP %>% 
  ggplot(., aes(log(GPPgC_f), logCH4_mgC, color = Site)) +
  geom_point(aes(), size = 1)+
    scale_x_continuous(limits = c(-1,2))+
        scale_color_manual(values = c("orange1", "royalblue2"))+
   geom_smooth(method = "lm", se = FALSE, aes(colour = Site), size = 0.5) +
  xlab(bquote('lnGPP (g C' ~m^-2~ day^-1*')'))+
    ylab(bquote('' ~lnFCH[4]~ ' (g C' ~m^-2~ day^-1*')'))+
    #scale_x_continuous(limits = c(- 2))+
    ggtitle("GPP")+
  theme_bw()+ 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 14)))

ggsave(file = "/Users/marionnyberg/Google\ Drive/Micromet\ Lab/People/2019-Marion\ Nyberg/BB1-2/plots/CH4GPP.jpeg", width = 5, height = 4, device='jpeg', dpi=300)

```